### 2016-09-12 ms.tex
first commit

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{bmpsize}
\usepackage[anythingbreaks]{breakurl}

\def\startdata{\if@table@not@headed\kill\caption{\\%
    \@tablecaption}\endhead\hline\endfoot%
  \fi%
}

\def\enddata{% 
 \crcr 
 \noalign{\vskip .7ex}% 
 \before@enddata 
 \endtabular 
 \setbox\pt@box\lastbox 
 \pt@width\wd\pt@box\box\pt@box 
}%

\newcommand{\aprx}{\raise.17ex\hbox{$\scriptstyle\sim$}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[SPIDERMAN]{SPIDERMAN}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
$^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
$^{2}$Department of Physics, University of America, America, America, America}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
planets and satellites: individual (WASP 52b)---stars: individual (WASP 52)---techniques: spectroscopic---planets and satellites: atmospheres---celestial mechanics---atmospheric effects
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}\label{sec:introduction}

BATMAN \citep{Kreidberg2015a}

\section{Observations}\label{sec:Observations}

\section{Method}\label{sec:method}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/b53.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

\subsection{Fitting procedure}\label{sec:fitting}

\section{Results}\label{sec:results}

\subsection{transmission spectra}

\subsection{Updated system parameters}\label{sec:system}

\section{Discussion}\label{sec:Discussion}

\subsection{Spot crossing event}\label{sec:spotcross}

\section{Conclusions}

\section*{Acknowledgements}

The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonothan Fortney and Pascale Geurard.

T.L. is supported by a STFC studentship. P.W. is supported by a STFC consolidated grant (ST/L000733/1).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
%\bibliography{/home/astro/phrmat/Documents/BibTeX/Papers-LowEUV}
\bibliography{bibliography}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%\appendix

%\section{Some extra material}

%If you want to present additional material which would interrupt the flow of %the main paper,
%it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2016-09-12 get_bib.sh

@@ -1,0 +1,1 @@
+cp /home/astro/phrmat/Documents/BibTeX/Papers-SPIDERMAN.bib bibliography.bib

### 2016-09-14 ms.tex
added lots of plots

@@
 \begin{center}
-\includegraphics[width=\columnwidth]{img/b53.pdf}
+\includegraphics[width=\columnwidth]{img/zhang_quad.pdf}
+\caption{This is a caption}
+\label{fig:zhang_quad}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/zhang_quad_bright.pdf}
+\caption{Same as \ref{fig:zhang_quad}, but the scale is now flux instead of temperature.
+A blackbody spectrum and a channel of 1.1-1.7 microns was assumed to make the conversion.
+The option exists to add limb darkening to this profile.}
+\label{fig:zhang_quad2}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
 \caption{This is a caption}
@@
 
+\subsection{Integrator validation}\label{sec:numerical}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/precision.pdf}
+\caption{This is a caption}
+\label{fig:extract_region}
+\end{center}
+\end{figure}
+
+\subsection{Performance}\label{sec:performance}
+
+In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core. This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.
+
+The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.
+
+\subsection{Performance}\label{sec:performance}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/exec_time.pdf}
+\caption{This is a caption}
+\label{fig:exec_time}
+\end{center}
+\end{figure}
+
 \section{Results}\label{sec:results}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/system.pdf}
+\caption{This is a caption}
+\label{fig:extract_region}
+\end{center}
+\end{figure}
 

### 2016-09-26 ms.tex
added plots
started to write some discussion

@@
 \usepackage[anythingbreaks]{breakurl}
+\usepackage{subfig}
+\usepackage{fancyvrb}
+\usepackage{hyperref}
 
@@
 % Keep the title short and informative.
-\title[SPIDERMAN]{SPIDERMAN}
+\title[spiderman]{\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.}
 
@@
 $^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
-$^{2}$Department of Physics, University of America, America, America, America}
+$^{2}$Department of Astronomy, Harvard, America, America, America}
 
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2015}
+\pubyear{2016}
 
@@
 
+Presenting \textsc{spiderman}, a fast code for calculating exoplanet phase curves and secondary eclipses with arbitrary surface brightness distributions.
+
+The development version of the code is available at \url{https://github.com/tomlouden/spiderman}.
+
 \end{abstract}
+
+\textsc{spiderman}
 
@@
 BATMAN \citep{Kreidberg2015a}
-
-\section{Observations}\label{sec:Observations}
 
@@
 \begin{center}
+\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
+\includegraphics[width=\columnwidth]{img/spherical_lc.pdf}
+\caption{A model generated using spherical harmonics}
+\label{fig:harmonics}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
@@
 \end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/zhang_lc_zoom.pdf}
+\caption{This is a caption}
+\label{fig:extract_region}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
+\caption{This is a caption}
+\label{fig:extract_region}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
+\caption{left: right: the constraints on the brightness distribution.}
+\label{fig:extract_region}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+\caption{The underlying temperature distributions generated by the zhang model.}
+\label{fig:extract_region}
+\end{center}
+\end{figure*}
 
@@
 
-\subsection{Performance}\label{sec:performance}
-
 \begin{figure}
@@
 
-\section{Results}\label{sec:results}
+\section{The \textsc{spiderman} package}\label{sec:package}
+
+\textsc{spiderman} is an open source project and is being actively developed on github.
+The code is available on PyPi, and the latest stable version can easily by installed by simply running the command
+
+\begin{Verbatim}[frame=single]
+> pip install spiderman-package
+\end{Verbatim}
+
+Or, to access the bleeding-edge development version from github:
+
+\begin{Verbatim}[frame=single]
+> git clone https://github.com/tomlouden/SPIDERMAN
+> cd SPIDERMAN
+> sudo python setup.py install
+\end{Verbatim}
+
+Full installation instructions and other information are available in the documentation, at \url{http://spiderman.readthedocs.io}
 
@@
 
-\subsection{transmission spectra}
+\section{Application to data}\label{sec:Observations}
 
-\subsection{Updated system parameters}\label{sec:system}
+As a test of the performance of the code the model was applied to a phase curve and secondary eclipse of WASP-43b taken with HST WFC3.
+These data had previously been published in \citet{Stevenson2014c}.
+However, in this paper the phase curve and the secondary eclipse are treated as seperate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
+Indeed, the bright dayside of the planet is the main driver of the phase curve, and is also the part occulted by the stellar disc.
+It is therefore more parsimonious, if at all possible, to use a model that accounts for both of these observations simultaneously.
+This also reduces the total number of paramters needed, which is satisfying from an information content angle.
+
+One could argue that planetary limb darkening, among other effects, will act to decouple the secondary eclipse from the phase curve, and there are not good constraints on what to expect from the limb darkening as it requires a full atmosphere model treatment.
+However, one would expect that the.
+\textsc{spiderman} does have the option to include planetary limb darkening, which would allow one to marginalise over the uncertainty in these parameters.
+
+In princple, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet.
 
@@
 
-\subsection{Spot crossing event}\label{sec:spotcross}
+\subsection{Future work}\label{sec:future work}
+
+\textsc{spiderman} is still under development, and there are a number of features that are planned to be implemented:
+
+- More brightness distributions, such as orange segments
+- Better treatment of errors in the
 

### 2016-10-11 ms.tex
new plots

@@
 
-\subsection{Fitting procedure}\label{sec:fitting}
+\subsection{Model design}\label{sec:fitting}
+
+The model is designed so that an arbitrary brightness distribution can be used, and that the resulting phase curve and secondary eclipse lightcurves can be calculated rapidly and accurately.
+
+The visible disc of the planet is divided into a series of annuli, and then these in turn are separated in theta.
+The number of segments in each annuli are chosen so that the area of every sector is the same.
+This results in 1 circular segment in the center, then 3 regions in the second annuli See the schematic in figure \ref{fig:schematic}.
+The planet is defined to have a radius of 1.
+Other grid schemes could be implemented in future versions, for example, if it is decided that the information content is higher in some parts of the planet than others then the grid could be made finer in these regions.
+
+In practice, it is found that dividing the planet into 5 radially (25 total sectors) gives results within a few percent of higher density grids, and is significantly faster.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
+\caption{Schematic representation of the planet grid. All sectors are equal area.}
+\label{fig:schematic}
+\end{center}
+\end{figure}
 
@@
 One could argue that planetary limb darkening, among other effects, will act to decouple the secondary eclipse from the phase curve, and there are not good constraints on what to expect from the limb darkening as it requires a full atmosphere model treatment.
-However, one would expect that the.
 \textsc{spiderman} does have the option to include planetary limb darkening, which would allow one to marginalise over the uncertainty in these parameters.
 
-In princple, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet.
+In principle, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet, however this would require a full radiative transfer treatment of the planet.
+
+WASP-43b appears to have a near isothermal profile \citep{Stevenson2014c}, which should correspon
+
+\section{Systematics model}\label{sec:systematics}
+
+The data are effectedThe systematics model is the same that was used in the previous treatment \citep{Stevenson2014c}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{img/systematics.pdf}
+\caption{Top: raw data from HST, the systematic components are all visible.
+second panel shows the physical model fit (red) and the systematic model (blue).
+The third panel shows the model fit to the data with the systematic noise component removed, the fourth panel is the residuals of the fit.
+}
+\label{fig:systematics}
+\end{center}
+\end{figure*}
+
+\section{MCMC}\label{sec:MCMC}
+
+To investigate the correlation between the
+
+In table \ref{tab:results}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/new_lc.pdf}
+\caption{The final fitted lightcurve. The primary transit is fit by \textsc{batman} and is off the scale of this figure.}
+\label{fig:extract_region}
+\end{center}
+\end{figure}
+
+\begin{center}
+\begin{table*}{
+\caption{This is my caption}
+\begin{center}
+\begin{tabular}{l c c c c c}
+\hline
+\hline
+          &   ld fixed   &             &   ld free    &             \\
+name      &   median     & error       &   median     & error        & unit        \\
+\hline
+Period &  0.813473977 & $\pm$ 0.000000036 &  0.813473979 & $\pm$ 0.000000034 & days\\
+$t0$ & 2456601.0274024 & $\pm$   0.0000091 & 2456601.0274025 & $\pm$   0.0000091 & days\\
+$a/R_*$ &       4.8762 & $\pm$      0.0089 &       4.8772 & $\pm$      0.0087 & -\\
+inclination &       82.123 & $\pm$       0.038 &       82.125 & $\pm$       0.037 & degrees\\
+eccentricity & 0 & - & 0 & - & -\\
+$R_p/R_*$ &     0.159692 & $\pm$    0.000093 &     0.159650 & $\pm$    0.000092 & -\\
+$u1$ &       0.3880 & $\pm$      0.0083 &       0.3875 & $\pm$      0.0082 & -\\
+$u2$ & 0 & - & 0 & - & -\\
+$c_1$ & 3.687319e+08 & $\pm$    0.000090e+08 & 3.687526e+08 & $\pm$    0.000089e+08 & -\\
+$c_2$ & 3.693661e+08 & $\pm$    0.000097e+08 & 3.693654e+08 & $\pm$    0.000097e+08 & -\\
+$c_3$ & 3.689717e+08 & $\pm$    0.000093e+08 &  3.68984e+08 & $\pm$     0.00010e+08 & -\\
+$v1_1$ &   -1.484e+06 & $\pm$       0.045e+06 &   -1.559e+06 & $\pm$       0.049e+06 & -\\
+$v1_2$ &    -6.31e+05 & $\pm$        0.50e+05 &    -6.19e+05 & $\pm$        0.55e+05 & -\\
+$v1_3$ &    -8.56e+05 & $\pm$        0.49e+05 &    -8.57e+05 & $\pm$        0.54e+05 & -\\
+$v2_1$ &    1.004e+06 & $\pm$       0.059e+06 &    1.076e+06 & $\pm$       0.064e+06 & -\\
+$v2_2$ &     1.83e+05 & $\pm$        0.61e+05 &     1.92e+05 & $\pm$        0.67e+05 & -\\
+$v2_3$ &     4.08e+05 & $\pm$        0.62e+05 &     3.77e+05 & $\pm$        0.67e+05 & -\\
+$r1$ &        123.2 & $\pm$         3.5 &        122.7 & $\pm$         3.5 & -\\
+$r2$ &        5.874 & $\pm$       0.011 &        5.877 & $\pm$       0.011 & -\\
+$r3$ &       -0.087 & $\pm$       0.028 &       -0.113 & $\pm$       0.028 & -\\
+scale &   -0.0024748 & $\pm$   0.0000061 &   -0.0024749 & $\pm$   0.0000060 & -\\
+$p_{u1}$ & 0 & - &         -1.2 & $\pm$         0.9 & -\\
+$p_{u2}$ & 0 & - &         -2.7 & $\pm$         1.1 & -\\
+$a$ &      0.01421 & $\pm$     0.00040 &      0.01419 & $\pm$     0.00040 & AU\\
+$\xi$ &        0.436 & $\pm$       0.050 &        0.417 & $\pm$       0.053 & -\\
+$T_n$ &         1290 & $\pm$          39 &         1069 & $\pm$          62 & K\\
+$\Delta_T$ &          699 & $\pm$          53 &          827 & $\pm$          92 & K\\
+$T_s$ &         4530 & $\pm$         120 &         4530 & $\pm$         120 & K\\
+\end{tabular}
+\end{center}
+\label{tab:results}
+}
+\end{table*}
+\end{center}
 

### 2016-10-12 ms.tex
working on introduction

@@
 
+Secondary eclipses and phase curves can give direct insight into the thermal transport processes, and vertical structure of an exoplanet atmosphere.
+
+Hot Jupiters are expected to be tidally locked to their parent stars, resulting in a permanent day and night side with enormous differences in incident flux.
+The details of the heat transport in the atmosphere will effect how efficiently energy can be transported between the two hemispheres of the planet.
+
+General Circulation Models, GCM's, are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.]{Showman2008}
+
+An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
+
+An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.
+This effect can also be mimicked by a high eccentricity (CITE?).
+
+\citet{Zhang2016} showed that this behaviour could be captured with a simple analytical formalism.
+
 BATMAN \citep{Kreidberg2015a}
+
+There does not currently exist an open source code for calculating secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
 
@@
 
-In practice, it is found that dividing the planet into 5 radially (25 total sectors) gives results within a few percent of higher density grids, and is significantly faster.
+In practice, it is found that dividing the planet into 5 radially (25 total sectors) gives results within a few percent of higher density grids, and is significantly faster to run.
+
+Each of the grid segments is a well defined geometric shape for which it is simple to calculate the fraction blocked by the planet passing behind the star, which in the model is represented as an occulting circle.
+
+The area of one of these geometrical segments that has been blocked by the star can always be calculated by breaking the area into a combination of circle segments and triangles, for which the areas are known.
+
+There are a small number of different general "cases" for the numbers of triangles and segments that must be used, that can be selected based on the number and types of "collision points" between the planet region and the stellar circle.
+Therefore, the first step for calculating the occulted area for each segment of the planet is to calculate these collision points.
+Within \textsc{spiderman} the region boandaries are stored as the radius of the inner and outer arcs, and the $\theta$ angle of the two radial lines.
+
+Finding the collision points between an arc or a line and a circle (the star), if any exist, are trivial and fast to calculate.
+The code then classifies the geometric "case" of the collision based on the number of collision points on the 4 boundary sides.
+
+For example, if there are two collision points between the outer arc and the edge of the star, then this falls into the case where the occulted area can be described by the sum of two circular segments.
+Other cases include larger numbers of components, but can still be described by a small number of circle segments and triangles.
+
+The advantage of this geometric approach is that the planet can be described by a small number of regions with no loss in numerical precision, enabling eclipses and phase curves to be calculated extremely rapidly.
 
@@
 \end{figure}
+
+\subsection{Available models}\label{sec:ttof}
+
+\subsection{Temperature to fluxes}\label{sec:ttof}
+
+Some physical models, such as the one adapted from \citep{zhang2016} are defined in terms of temperature, where of course the observable that is being fit for is the emitted flux.
+Therefore, it is necessary
+
+If we make the assumption that the temperature distribution maps to the \emph{brightness temperature} distribution, then we can recover these fluxes. This will be valid for narrow
+
+An additional factor that is not currently considered by the model but will be featured in future releases of the code is to also include the ability for the user to define instrument response functions as a function of wavelength.
+
+\subsection{}\label{sec:ttof}
 
@@
 
-WASP-43b appears to have a near isothermal profile \citep{Stevenson2014c}, which should correspon
+WASP-43b appears to have a near isothermal profile \citep{Stevenson2014c}, which should correspond to a zero limb darkening.
+However, as I show in section X.
+there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
+
+During the MCMC fit I place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
+This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
+\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
+\label{fig:limb brighten}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/model.pdf}
+\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
+\label{fig:model}
+\end{center}
+\end{figure}
 
@@
 
-The data are effectedThe systematics model is the same that was used in the previous treatment \citep{Stevenson2014c}.
+As with most exoplanet observations with Hubble, the data are effected by the idiosyncratic systematic errors of the instrument.
+Fortunately, the sources of these errors are relatively well understood, and are generally quite repeatable between observations.
+They are therefore quite straightforward to fit for and remove.
+
+The systematics model is the same that was used in the previous treatment \citep{Stevenson2014c}.
+
+In brief, there are three components to the systematics model:
+
+1. Scan direction offset
+
+There is an offset in the recorded flux depending on which way the the ccd was scanning during the readout, in one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the offset.
+This leads to a very repeatable offset in the fluxes between the two scan directions, which can be captured with a single parameter "scale"
+
+2. Orbit long "hook effect"
+
+\begin{equation} \label{eq:hook}
+F_{cor} = F*(1-exp(-r1 t_{orb}-r2-r3 \delta_{fo}))
+\end{equation}
+
+Where $F$ is the flux before correction and $F_{cor}$ is the corrected flux $t_{orb}$ is the time from the start of each \emph{obit}, $r1$, $r2$, $r3$ are the fitted coefficients.
+This exponential ramp has a different shape during the first orbit of a visit, so the $\delta_{fo}$ function takes a value of 1 if the orbit is the first, and 0 at all other times.
+
+The exponential hook shape is believed to be related to charge trapping, and is a characteristic and repeatable feature across orbits, so these parameters are fit simultaneously over visits.
+
+3. A visit long slope.
+
+Each visit displays a decreasing slope, which is modelled as a second order polynomial.
+The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \cite{Wakeford2016}.
+Here, they are also likely blended with the "Breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
+The shape of these visit long effects is slightly different between the three visits used here, so the three paramters of the polynomial are fit seperately for the three visits.
+
+The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planets phase curve, so there is potential for serious degeneracies between the systematics and the physical model.
+
+Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy.
+As can be seen in the large corner plot in figure \ref{}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
+
+Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in (REF), this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
 
@@
 In table \ref{tab:results}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{img/huge_triangle.pdf}
+\caption{stupidly big triangle plot1}
+\label{fig:extract_region}
+\end{center}
+\end{figure*}
 
@@
 
-- More brightness distributions, such as orange segments
-- Better treatment of errors in the
+- More thermal brightness distributions, such as orange segments and a simple parameterised hotspot (etc?)
+- Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
+- Allow calculation of multiple spectral channels simultaneously, with linked system parameters.
+- Include instrument response in calculating flux ratios
+- Better treatment of errors in the spectral energy distribution of the star - include errors in log-g and Metalicity
+
+In regards to the re-analysis of WASP-43bs phase curve, future analysis will focus on
+
+- Confirming the detected flux on the nightside is a real feature and not an artefact
+- Further test for degeneracies between HST systematics and the physical model of the phase curve, in particular the combination of visit long slope and breathing modes.
+This could be accomplished by a Gaussian process analysis.
 

### 2016-10-13 ms.tex
written some methods

@@
 
+\textsc{spiderman}
+
 The development version of the code is available at \url{https://github.com/tomlouden/spiderman}.
@@
 
-\textsc{spiderman}
-
 % Select between one and six entries from the list of approved keywords.
@@
 \begin{keywords}
-planets and satellites: individual (WASP 52b)---stars: individual (WASP 52)---techniques: spectroscopic---planets and satellites: atmospheres---celestial mechanics---atmospheric effects
+%planets and satellites: individual (WASP 43b)---stars: individual (WASP 43)---techniques: spectroscopic---planets and satellites: atmospheres---celestial mechanics---atmospheric effects
 \end{keywords}
@@
 
-General Circulation Models, GCM's, are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.]{Showman2008}
+The planets are hot enough that they have appreciable infrared flux emission, with contrasts with their parents stars of order 0.1\%, making detection with current generation instruments feasible.
+\citet{Deming2005} detected the infrared flux of HD\,209458b by observing the secondary transit of the planet with the MIPS instrument on \emph{Spitzer}.
+Using the IRAC instrument on \emph{Spitzer}, \citet{Knutson2007b} went on to measure the secondary eclipse of HD\,189733b with high precision, and also show that the system displayed a sinusoidal \emph{phase curve}, caused by the bright regions of the planet rotating into and out of view.
+Intriguingly, the phase of this sinusoidal curve was significantly offset from the time of secondary eclipse, validating earlier predictions from GCM's.
+
+Excitingly, it is possible to invert phase curves to give information on the longitudinal brightness distribution of the exoplanet, providing a way to map the surfaces of other worlds.
+
+\cite{Majeau2012} showed that as well as mapping longitudinally with phase curves, it is possible to get a two dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non zero impact parameter.
+This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress.
+The brightness distribution of the planet's permanent dayside will be imprinted on the precise shape of the ingress and egress curves.
+
+There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
+$\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
+\citep{Harrington2006,Cowan2007,zellem2014}.
+WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
+The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be reanalysed here.
+
+The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
+
+\citep[e.g.][]{Showman2015}
+
+General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}
 
@@
 \includegraphics[width=\columnwidth]{img/zhang_quad.pdf}
-\caption{This is a caption}
+\caption{An example of the temperature distribution generated by using the Zhang model. Clockwise from top left: Phase = 0.0,0.25,0.75,1.0}
 \label{fig:zhang_quad}
@@
 \includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
-\caption{This is a caption}
-\label{fig:extract_region}
+\caption{An example lightcurve generated using the distribution in figure \ref{fig:zhang_quad}}
+\label{fig:zhang_lc}
 \end{center}
@@
 \includegraphics[width=\columnwidth]{img/zhang_lc_zoom.pdf}
-\caption{This is a caption}
-\label{fig:extract_region}
+\caption{A close up of the secondary eclipse in figure \ref{fig:zhang_lc}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
+\label{fig:zhang_zoom}
 \end{center}
@@
 \includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
-\caption{This is a caption}
-\label{fig:extract_region}
+\caption{A section of the larger corner plot in figure \ref{fig:big triangle}.
+The parameters for the Zhang model fit are loosely correlated.
+The distribution for the stellar temperature, $T_s$, is set by the prior}
+\label{fig:triangle corner sub}
 \end{center}
@@
 \caption{left: right: the constraints on the brightness distribution.}
-\label{fig:extract_region}
+\label{fig:best_fit_flux}
 \end{center}
@@
 \caption{The underlying temperature distributions generated by the zhang model.}
-\label{fig:extract_region}
+\label{fig:best_fit_temp}
 \end{center}
@@
 \includegraphics[width=\columnwidth]{img/precision.pdf}
-\caption{This is a caption}
-\label{fig:extract_region}
+\caption{A comparison between a uniform flux distribution eclipse model generated with 400 segments and a single segment.
+If the integrator is correct, then there should be no difference between these two models.
+The bottom panel shows that the results are identical, apart from errors at the level of floating point precision (dotted lines) during ingress and egress.}
+\label{fig:precision}
 \end{center}
@@
 \includegraphics[width=\columnwidth]{img/exec_time.pdf}
-\caption{This is a caption}
+\caption{The speed with which a model with 1000 timepoints can be generated}
 \label{fig:exec_time}
@@
 
-Some physical models, such as the one adapted from \citep{zhang2016} are defined in terms of temperature, where of course the observable that is being fit for is the emitted flux.
+Some physical models, such as the one adapted from \citep{Zhang2016} are defined in terms of temperature, where of course the observable that is being fit for is the emitted flux.
 Therefore, it is necessary
@@
 
+typing the command
+
+\begin{Verbatim}[frame=single]
+> spider_params.plot\_system()
+\end{Verbatim}
+
+will generate a plot like figure \ref{fig:plot_system}
+
 \begin{figure}
@@
 \includegraphics[width=\columnwidth]{img/system.pdf}
-\caption{This is a caption}
-\label{fig:extract_region}
+\caption{An example of the graphical output that \textsc{spiderman} can produce.
+This image is a scale representation of the system, with the planetary flux map included.
+This is useful for visualising the model.
+It was generated with the spiderman.plot\_system() command.
+The image of the star is purely aesthetic, and does not contain any model detail.}
+\label{fig:plot_system}
 \end{center}
 \end{figure}
+
+\textsc{spiderman} has been designed to ensure that it is easy to visualise the appearance of the model at all stages.
 
@@
 As a test of the performance of the code the model was applied to a phase curve and secondary eclipse of WASP-43b taken with HST WFC3.
-These data had previously been published in \citet{Stevenson2014c}.
+These data had previously been published in \citet{Stevenson2014}.
 However, in this paper the phase curve and the secondary eclipse are treated as seperate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
@@
 
-WASP-43b appears to have a near isothermal profile \citep{Stevenson2014c}, which should correspond to a zero limb darkening.
+WASP-43b appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to a zero limb darkening.
 However, as I show in section X.
@@
 
-The systematics model is the same that was used in the previous treatment \citep{Stevenson2014c}.
+The systematics have effects on scales of \emph{visits}, \emph{orbits} and individual exposures, where a visit is a continuous set of orbits directed at a target.
+Due to the low earth orbit of Hubble, each complete orbit lasts 95 minutes, and for approximately half of this time the target will be unobservable due to being behind the Earth.
+For this reason, a complete exoplanet transit can not be observed with one "visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.
+
+In this study, three visits, each with 12 orbits was used to cover the full phase of WASP-43.
+The phasing can be seen in figure \ref{fig:systematics}, and a phase folded lightcurve can be seen in figure \ref{fig:phase folded}
+
+The systematics model we use to fit WASP-43 is the same that was used in the previous treatment \citep{Stevenson2014}.
 
@@
 There is an offset in the recorded flux depending on which way the the ccd was scanning during the readout, in one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the offset.
-This leads to a very repeatable offset in the fluxes between the two scan directions, which can be captured with a single parameter "scale"
+This leads to a very repeatable offset in the fluxes between the two scan directions, which can be captured with a single parameter \emph{scale}
 
 2. Orbit long "hook effect"
+
+Each orbit displays a characteristic exoplential "hook" signal, which can be modelled as
 
@@
 
-Each visit displays a decreasing slope, which is modelled as a second order polynomial.
+Each \emph{visit} displays a decreasing slope, which is modelled as a second order polynomial.
 The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \cite{Wakeford2016}.
@@
 Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in (REF), this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/new_lc.pdf}
+\caption{The final fitted lightcurve. The primary transit is fit by \textsc{batman} and is off the scale of this figure.}
+\label{fig:phase folded}
+\end{center}
+\end{figure}
 
@@
 \caption{stupidly big triangle plot1}
-\label{fig:extract_region}
+\label{fig:big triangle}
 \end{center}
 \end{figure*}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/new_lc.pdf}
-\caption{The final fitted lightcurve. The primary transit is fit by \textsc{batman} and is off the scale of this figure.}
-\label{fig:extract_region}
-\end{center}
-\end{figure}
 
@@
 This could be accomplished by a Gaussian process analysis.
+- Perform recovery with a non-informative model, such as spherical harmonics, and see if the recovered brightness or temperature maps are the same as recovered through physical models.
+- Investigating the apparent preference for limb brightened profiles in the model fit. This may be evidence of
 

### 2016-10-17 ms.tex
abstract

@@
 
-\textsc{spiderman}
+Using a geometrical algorithm, the code solves exactly the area of sections of the disc of the planet that are occulted by the star.
+The code is written in C and optimised to run extremely quickly, with no loss in precision.
+Approximately 1000 models can be generated per second with typical parameters.
+
+Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints of the physics of the atmosphere, such as the ratio between advective and radiative timescales.
 

### 2016-10-17 ms.tex
examples

@@
 
+\textsc{spiderman} comes prepackaged with several plotting scripts to make visualisation of the model simple.
+
 typing the command
@@
 \begin{Verbatim}[frame=single]
-> spider_params.plot\_system()
+> spider_params.plot_planet()
 \end{Verbatim}
 
-will generate a plot like figure \ref{fig:plot_system}
+Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date.
+
+typing the command
+
+\begin{Verbatim}[frame=single]
+> spider_params.plot_system()
+\end{Verbatim}
+
+will generate a plot like figure \ref{fig:plot_system}, which is a scale diagram of the system.
+The desired phase or julian date can be given as an argument.
+These plots can be very useful for visualising the physical impacts of
 

### 2016-10-18 ms.tex
examples
finalised figures

@@
 \begin{center}
-\includegraphics[width=\columnwidth]{img/zhang_quad.pdf}
-\caption{An example of the temperature distribution generated by using the Zhang model. Clockwise from top left: Phase = 0.0,0.25,0.75,1.0}
-\label{fig:zhang_quad}
+\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
+\caption{Schematic representation of the planet grid. All sectors are equal area.}
+\label{fig:schematic}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{img/zhang_quad_bright.pdf}
-\caption{Same as \ref{fig:zhang_quad}, but the scale is now flux instead of temperature.
-A blackbody spectrum and a channel of 1.1-1.7 microns was assumed to make the conversion.
-The option exists to add limb darkening to this profile.}
-\label{fig:zhang_quad2}
+\includegraphics[width=\columnwidth]{img/precision.pdf}
+\caption{A comparison between a uniform flux distribution eclipse model generated with 400 segments and a single segment.
+If the integrator is correct, then there should be no difference between these two models.
+The bottom panel shows that the results are identical, apart from errors at the level of floating point precision (dotted lines) during ingress and egress.}
+\label{fig:precision}
 \end{center}
@@
 \includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
-\includegraphics[width=\columnwidth]{img/spherical_lc.pdf}
 \caption{A model generated using spherical harmonics}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
-\caption{An example lightcurve generated using the distribution in figure \ref{fig:zhang_quad}}
-\label{fig:zhang_lc}
+\includegraphics[width=\columnwidth]{img/both_lc.pdf}
+\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
+\caption{A close up of the secondary eclipse in figure \ref{fig:ex_lcs}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
+\label{fig:ex_lcs}
 \end{center}
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/zhang_lc_zoom.pdf}
-\caption{A close up of the secondary eclipse in figure \ref{fig:zhang_lc}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
-\label{fig:zhang_zoom}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
-\caption{A section of the larger corner plot in figure \ref{fig:big triangle}.
-The parameters for the Zhang model fit are loosely correlated.
-The distribution for the stellar temperature, $T_s$, is set by the prior}
-\label{fig:triangle corner sub}
-\end{center}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
-\caption{left: right: the constraints on the brightness distribution.}
-\label{fig:best_fit_flux}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
-\caption{The underlying temperature distributions generated by the zhang model.}
-\label{fig:best_fit_temp}
-\end{center}
-\end{figure*}
-
-\subsection{Model design}\label{sec:fitting}
+\subsection{integrator design}\label{sec:integrator}
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
-\caption{Schematic representation of the planet grid. All sectors are equal area.}
-\label{fig:schematic}
-\end{center}
-\end{figure}
-
 \subsection{Integrator validation}\label{sec:numerical}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/precision.pdf}
-\caption{A comparison between a uniform flux distribution eclipse model generated with 400 segments and a single segment.
-If the integrator is correct, then there should be no difference between these two models.
-The bottom panel shows that the results are identical, apart from errors at the level of floating point precision (dotted lines) during ingress and egress.}
-\label{fig:precision}
-\end{center}
-\end{figure}
+\subsection{Flux conversions}\label{sec:flux conversions}
+
+\subsection{Stellar models}\label{sec:stellar models}
 
@@
 Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date.
+If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[width=\columnwidth]{img/system.pdf}
+\includegraphics[width=\textwidth]{img/system.pdf}
 \caption{An example of the graphical output that \textsc{spiderman} can produce.
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
-\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
-\label{fig:limb brighten}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/model.pdf}
-\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
-\label{fig:model}
-\end{center}
-\end{figure}
 
@@
 Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy.
-As can be seen in the large corner plot in figure \ref{}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
+As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
 
 Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in (REF), this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/new_lc.pdf}
-\caption{The final fitted lightcurve. The primary transit is fit by \textsc{batman} and is off the scale of this figure.}
-\label{fig:phase folded}
-\end{center}
-\end{figure}
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/new_lc.pdf}
+\caption{The final fitted lightcurve. The primary transit is fit by \textsc{batman} and is off the scale of this figure.}
+\label{fig:phase folded}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
+\caption{left: right: the constraints on the brightness distribution.}
+\label{fig:best_fit_flux}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+\caption{The underlying temperature distributions generated by the zhang model.}
+\label{fig:best_fit_temp}
+\end{center}
+\end{figure*}
+
 \section{MCMC}\label{sec:MCMC}
@@
 In table \ref{tab:results}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
+\caption{A section of the larger corner plot in figure \ref{fig:big triangle}.
+The parameters for the Zhang model fit are loosely correlated.
+The distribution for the stellar temperature, $T_s$, is set by the prior}
+\label{fig:triangle corner sub}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/model.pdf}
+\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
+\label{fig:model}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
+\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
+\label{fig:limb brighten}
+\end{center}
+\end{figure}
 
@@
 
-T.L. is supported by a STFC studentship. P.W. is supported by a STFC consolidated grant (ST/L000733/1).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-18 ms.tex
final structure

@@
 WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
-The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be reanalysed here.
+The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be re-analysed here.
 
@@
 An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.
-This effect can also be mimicked by a high eccentricity (CITE?).
+This effect can also be mimicked by a high eccentricity.
 
@@
 
-\section{Method}\label{sec:method}
+\section{The model}\label{sec:the model}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
-\caption{Schematic representation of the planet grid. All sectors are equal area.}
-\label{fig:schematic}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/precision.pdf}
-\caption{A comparison between a uniform flux distribution eclipse model generated with 400 segments and a single segment.
-If the integrator is correct, then there should be no difference between these two models.
-The bottom panel shows that the results are identical, apart from errors at the level of floating point precision (dotted lines) during ingress and egress.}
-\label{fig:precision}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
-\caption{A model generated using spherical harmonics}
-\label{fig:harmonics}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/both_lc.pdf}
-\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
-\caption{A close up of the secondary eclipse in figure \ref{fig:ex_lcs}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
-\label{fig:ex_lcs}
-\end{center}
-\end{figure}
-
-\subsection{integrator design}\label{sec:integrator}
+\subsection{Integrator design}\label{sec:integrator}
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
+\caption{Schematic representation of the planet grid. All sectors are equal area.}
+\label{fig:schematic}
+\end{center}
+\end{figure}
+
 \subsection{Integrator validation}\label{sec:numerical}
 
-\subsection{Flux conversions}\label{sec:flux conversions}
+To test that the integrator is working correctly, a simple test was conducted.
+Assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have zero impact on the final light-curve.
+With a large number of segments and time points, all geometrical cases will be met, and it will quickly become obvious if there is a mistake in how the areas have been calculated.
 
-\subsection{Stellar models}\label{sec:stellar models}
+We compare the case of a single segment model, i.e., a circle, for which there is a single analytical solution to the area blocked by another circle, to one with 400 segments.
+In both cases the planet is assumed to have a total luminosity that is 1\% that of the star's.
 
-\subsection{Performance}\label{sec:performance}
-
-In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core. This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.
-
-The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.
+A lightcurve is calculated for each of these cases, and then the difference is taken.
+The results of this test can be seen in figure \ref{fig:precision}, where it is clear that there is no difference between the two lightcurves greater than floating point precision (2.22e-16).
+We therefore consider the geometric integrator of \textsc{spiderman} to be validated.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{img/exec_time.pdf}
-\caption{The speed with which a model with 1000 timepoints can be generated}
-\label{fig:exec_time}
+\includegraphics[width=\columnwidth]{img/precision.pdf}
+\caption{A comparison between a uniform flux distribution eclipse model generated with 400 segments and a single segment.
+If the integrator is correct, then there should be no difference between these two models.
+The bottom panel shows that the results are identical, apart from errors at the level of floating point precision (dotted lines) during ingress and egress.}
+\label{fig:precision}
 \end{center}
@@
 
-\subsection{Available models}\label{sec:ttof}
+\subsection{The temperature model}\label{sec:temp model}
+
+While \textsc{spiderman} has several different ways to model the
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/both_lc.pdf}
+\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
+\caption{A close up of the secondary eclipse in figure \ref{fig:ex_lcs}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
+\label{fig:ex_lcs}
+\end{center}
+\end{figure}
+
+Spherical projection:
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
+\caption{A model generated using spherical harmonics}
+\label{fig:harmonics}
+\end{center}
+\end{figure}
 
@@
 
-If we make the assumption that the temperature distribution maps to the \emph{brightness temperature} distribution, then we can recover these fluxes. This will be valid for narrow
+If we make the assumption that the temperature distribution maps to the \emph{brightness temperature} distribution, then we can recover these fluxes.
+This will be valid for band passes that are narrower than potentially strong molecular bands in the spectrum, such as water or carbon monoxide, but this assumption may introduce systematic errors into very wide band-passes.
 
@@
 
-\subsection{}\label{sec:ttof}
+\subsection{Stellar model}\label{sec:stellar model}
+
+Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, lightcurves can comfortably be fit by very unphysical planet and star fluxes, so long as the ratio between them is of the right order, and there will clearly be an enormous degeneracy between the planet and star brightness.
+
+In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.
+
+Both planets and stars, of course, do not act exactly like ideal black-body radiators.
+For the planet the brightness temperature, or the temperature of a perfect blackbody emitting the same amount of flux within a bandpass, is a widely used convention, and is the direct observable.
+
+For the star however, we can do better than this.
+From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, and therefore the stellar type.
+
+\textsc{spiderman} models the absolute luminosity of the star.
 
@@
 
-\section{Application to data}\label{sec:Observations}
+\subsection{Performance}\label{sec:performance}
+
+In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core. This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.
+
+The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/exec_time.pdf}
+\caption{The speed with which a model with 1000 timepoints can be generated}
+\label{fig:exec_time}
+\end{center}
+\end{figure}
+
+\subsection{Available models}\label{sec:ttof}
+
+\section{Application to data}\label{sec:Application}
 
@@
 These data had previously been published in \citet{Stevenson2014}.
-However, in this paper the phase curve and the secondary eclipse are treated as seperate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
+However, in this paper the phase curve and the secondary eclipse are treated as separate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
 Indeed, the bright dayside of the planet is the main driver of the phase curve, and is also the part occulted by the stellar disc.
 It is therefore more parsimonious, if at all possible, to use a model that accounts for both of these observations simultaneously.
-This also reduces the total number of paramters needed, which is satisfying from an information content angle.
+This also reduces the total number of parameters needed, which implies a better information content.
 
@@
 WASP-43b appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to a zero limb darkening.
-However, as I show in section X.
-there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
+However, as discussed in \ref{sec:discussion}, I will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
 
-During the MCMC fit I place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
-This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
-
-\section{Systematics model}\label{sec:systematics}
+\subsection{Systematics model}\label{sec:systematics}
 
@@
 In brief, there are three components to the systematics model:
-
-1. Scan direction offset
+\subsection*{1.) Scan direction offset}
 
@@
 
-2. Orbit long "hook effect"
+\subsection*{2.) Orbit long ``hook effect''}
 
-Each orbit displays a characteristic exoplential "hook" signal, which can be modelled as
-
+Each orbit displays a characteristic exoplential ``hook'' signal, which can be modelled as
 \begin{equation} \label{eq:hook}
@@
 \end{equation}
-
 Where $F$ is the flux before correction and $F_{cor}$ is the corrected flux $t_{orb}$ is the time from the start of each \emph{obit}, $r1$, $r2$, $r3$ are the fitted coefficients.
@@
 
-3. A visit long slope.
+\subsection*{3.) Visit long slope. }
 
@@
 The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \cite{Wakeford2016}.
-Here, they are also likely blended with the "Breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
+Here, they are also likely blended with the ``Breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
 The shape of these visit long effects is slightly different between the three visits used here, so the three paramters of the polynomial are fit seperately for the three visits.
@@
 Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy.
-As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
+As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.\\
 
-Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in (REF), this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
+Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in \citet{Gibson2012a}, this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{img/systematics.pdf}
-\caption{Top: raw data from HST, the systematic components are all visible.
-second panel shows the physical model fit (red) and the systematic model (blue).
-The third panel shows the model fit to the data with the systematic noise component removed, the fourth panel is the residuals of the fit.
-}
-\label{fig:systematics}
-\end{center}
-\end{figure*}
+\subsection{MCMC}\label{sec:MCMC}
+
+The only way to properly access the errors on the parameter values of interest, and test for degeneracies
+
+During the MCMC fit I place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
+This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
+
+For both models, the MCMC was run for 10 million steps, with the first 200,000 steps were discarded as burn in.
+
+\subsection{Results}\label{sec:results}
+
+In table \ref{tab:results}
 
@@
 \end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
-\caption{left: right: the constraints on the brightness distribution.}
-\label{fig:best_fit_flux}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
-\caption{The underlying temperature distributions generated by the zhang model.}
-\label{fig:best_fit_temp}
-\end{center}
-\end{figure*}
-
-\section{MCMC}\label{sec:MCMC}
-
-To investigate the correlation between the
-
-In table \ref{tab:results}
 
@@
 \end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/model.pdf}
-\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
-\label{fig:model}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
-\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
-\label{fig:limb brighten}
-\end{center}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{img/huge_triangle.pdf}
-\caption{stupidly big triangle plot1}
-\label{fig:big triangle}
-\end{center}
-\end{figure*}
 
@@
 
-\section{Discussion}\label{sec:Discussion}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
+\caption{left: right: the constraints on the brightness distribution, for the model where the planetary limb darkening was switched off.}
+\label{fig:best_fit_flux}
+\end{center}
+\end{figure*}
 
-\subsection{Future work}\label{sec:future work}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+\caption{The underlying temperature distributions generated by the zhang model.}
+\label{fig:best_fit_temp}
+\end{center}
+\end{figure*}
+
+\subsection{Discussion}\label{sec:Discussion}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/model.pdf}
+\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
+\label{fig:model}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
+\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
+\label{fig:limb brighten}
+\end{center}
+\end{figure}
+
+\section{Future work}\label{sec:future work}
 
@@
 
-- More thermal brightness distributions, such as orange segments and a simple parameterised hotspot (etc?)
-- Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
-- Allow calculation of multiple spectral channels simultaneously, with linked system parameters.
-- Include instrument response in calculating flux ratios
-- Better treatment of errors in the spectral energy distribution of the star - include errors in log-g and Metalicity
+\begin{itemize}
+\item More thermal brightness distributions, such as an "orange segments" model and a simple parametrised hotspot which can be offset in latitude and longitude
+\item Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
+\item Allow calculation of multiple spectral channels simultaneously, with linked system parameters.
+\item Include instrument response in calculating flux ratios
+\item Better treatment of errors in the spectral energy distribution of the star - include errors in log-g and Metalicity
+\end{itemize}
 
-In regards to the re-analysis of WASP-43bs phase curve, future analysis will focus on
+In regards to the re-analysis of WASP-43bs phase curve, future analysis will focus on:
 
-- Confirming the detected flux on the nightside is a real feature and not an artefact
-- Further test for degeneracies between HST systematics and the physical model of the phase curve, in particular the combination of visit long slope and breathing modes.
+\begin{itemize}
+\item Confirming the detected flux on the nightside is a real feature and not an artefact
+\item Further test for degeneracies between HST systematics and the physical model of the phase curve, in particular the combination of visit long slope and breathing modes.
 This could be accomplished by a Gaussian process analysis.
-- Perform recovery with a non-informative model, such as spherical harmonics, and see if the recovered brightness or temperature maps are the same as recovered through physical models.
-- Investigating the apparent preference for limb brightened profiles in the model fit. This may be evidence of
+\item Perform recovery with a non-informative model, such as spherical harmonics, and see if the recovered brightness or temperature maps are the same as recovered through physical models.
+\item Investigating the apparent preference for limb brightened profiles in the model fit.
+This is characteristic of a temperature inversion, but since there is no evidence for this in other data on WASP-43b it may be more likely that it indicates a weakness of the model.
+\item Making wavelength resolved maps.
+This will allow spectra as a function of latitude and longitude to be created.
+The wavelength also functions as a proxy for height in a planetary atmosphere, so the map will effectively be three dimensional.
+\item Investigate correlations between spectrally resolved bins and consider the impact of simultaneous fits.
+\end{itemize}
 
-\section{Conclusions}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{img/systematics.pdf}
+\caption{Top: raw data from HST, the systematic components are all visible.
+second panel shows the physical model fit (red) and the systematic model (blue).
+The third panel shows the model fit to the data with the systematic noise component removed, the fourth panel is the residuals of the fit.
+}
+\label{fig:systematics}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{img/huge_triangle.pdf}
+\caption{stupidly big triangle plot1}
+\label{fig:big triangle}
+\end{center}
+\end{figure*}
 

### 2016-10-18 ms.tex
stellar brightness

@@
 In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.
+Somewhat counter-intuitively, these constraints only need to be \emph{as a function of surface area}, i.e., on the specific intensity of the system components, not on their total luminosity.
+
+To see that this is indeed the case, consider a case where the radii of both the planet and the star have both been underestimated by a factor of 2, such that the total luminosity will have been underestimated by a factor of 4.
+If the planetary and stellar specific flux distributions remains the same, The secondary eclipse depth and phase curve amplitude both scale as $(R_p / R_*)^2$, so are unchanged.
+
+$(R_p / R_*)^2$ is of course constrained well by the primary transit.
 
@@
 
-For the star however, we can do better than this.
-From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, and therefore the stellar type.
+For the star however, we can do better than this. From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star
 

### 2016-10-19 ms.tex
csc broken

--- 2016-10-18 ms.tex
@@
 
-While \textsc{spiderman} has several different ways to model the
+\textsc{spiderman} has several different ways to model the brightness distribution, including a simple uniform distribution, and a non-informative model based on spherical harmonics (displayed visually in figure \ref{fig:harmonics}).
+However, the most interesting application is the physical model developed by \citet{Zhang2016}.
+This model was developed as part of a simple analytical framework to describe the broad trends within complex GCM's, and does a remarkably good job of replicating the temperature distributions of GCM's with only three free parameters.
+These parameters are physical in nature, the Temperature of the nightside of the planet, $T_n$, the difference in Temperature between the day and night side, $\Delta T$, and the ratio between the advective and radiative timescales in the atmosphere, $\xi$.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/both_lc.pdf}
-\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
-\caption{A close up of the secondary eclipse in figure \ref{fig:ex_lcs}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
-\label{fig:ex_lcs}
-\end{center}
-\end{figure}
+\textsc{spiderman} projects this temperature map onto the visible sphere of the planet, meaning it is used directly to calculate the secondary eclipse and phase curve.
+This is the first time a physical model of atmosphere circulation has been used to directly fit to data.
 
-Spherical projection:
+The $\xi$ parameter is perhaps the most interesting, as it effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere.
+The effects of this can be seen in \ref{fig:ex_lcs}, where
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/both_lc.pdf}
+\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
+\caption{The phase curve and secondary eclipses of an example planet generated with a simple spherical harmonics flux model (blue dashed) and the \citet{Zhang2016} physical model (red dot).
+Note in the physical model how the brightest point of the phase curve is significantly offset from the time of secondary transit, and the slightly different shape of the ingress and egress, both caused by the asymmetry in the flux distribution on the planet.}
+\label{fig:ex_lcs}
+\end{center}
+\end{figure}
+
 \subsection{Temperature to fluxes}\label{sec:ttof}
@@
 Some physical models, such as the one adapted from \citep{Zhang2016} are defined in terms of temperature, where of course the observable that is being fit for is the emitted flux.
-Therefore, it is necessary
+Therefore, it is necessary to convert from one to the other.
 
@@
 This will be valid for band passes that are narrower than potentially strong molecular bands in the spectrum, such as water or carbon monoxide, but this assumption may introduce systematic errors into very wide band-passes.
+
+We treat the planet as a ideal blackbody, which is clearly a simplification.
+For the planet the brightness temperature, or the temperature of a perfect blackbody emitting the same amount of flux within a bandpass, is a widely used convention, and is the direct observable.
+
+The total flux emitted by a blackbody has a trivial solution, however, \textsc{spiderman} is intended to model the observations of real instuments, which will of course only sample a very small sample of the electromagnetic spectrum.
+There is not an analytical expression for the total amount of flux emitted by a blackbody within an arbitrary wavelength band.
 
@@
 
-Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, lightcurves can comfortably be fit by very unphysical planet and star fluxes, so long as the ratio between them is of the right order, and there will clearly be an enormous degeneracy between the planet and star brightness.
+Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, lightcurves can comfortably be fit by very unphysical planet and star fluxes, so long as the ratio between them is of the right order.
+There will clearly be an enormous degeneracy between the planet and star brightness.
 
 In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.
+Somewhat counter-intuitively, these constraints only need to be on flux \emph{as a function of surface area}, i.e., on the specific intensity of the system components, and on their radius ratio, not on their total luminosity or radii.
 
-Both planets and stars, of course, do not act exactly like ideal black-body radiators.
-For the planet the brightness temperature, or the temperature of a perfect blackbody emitting the same amount of flux within a bandpass, is a widely used convention, and is the direct observable.
+To see that this is indeed the case, consider a situation where the radii of both the planet and the star have both been underestimated by a factor of 2, but their surface intensities are unchanged, such that the total luminosity will have been underestimated by a factor of 4.
+The secondary eclipse depth and phase curve amplitude both scale as $(R_p / R_*)^2$, so are unchanged.
+$(R_p / R_*)^2$ is of course constrained well by the primary transit.
+The surface brightness distribution as a function of longitude and latitude can therefore be recovered without any constraint on the absolute radii or luminosity of the components.
 
 For the star however, we can do better than this.
-From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, and therefore the stellar type.
+From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, which allow the observed stellar spectrum to be matched to a model spectra with physical units.
+This fixes the flux scale of the system, allowing useful constraints to be placed on the absolute flux level of the planet by extension.
 
-\textsc{spiderman} models the absolute luminosity of the star.
+\textsc{spiderman} models the stellar spectrum using a grid of PHOENIX stellar atmospheres calculated by \citet{Husser2013}.
+Using the user provided wavelength bandpass, \textsc{spiderman} calculates the total flux in this bandpass for the available models as a function of effective temperature, it then interpolates using a simple spline fit to calculate the flux for the effective temperature of the star.
+Internally, this is multiplied by the stellar radius to get an absolute flux level for the system.
+
+At present \textsc{spiderman} only interpolates in temperature, and picks the closest surface gravity and metalicity in the table, which will lead to small errors in the fluxes.
+Future versions of the code will interpolate in these values as well, allowing an MCMC to better model the uncertainty on the stellar surface brightness.
+
+\subsection{Lightcurve calculation}\label{sec:lightcurve}
+
+The primary purpose of \textsc{spiderman} is to produce lightcurves to compare with the data.
+Now that the functioning of the geometric integrator has been described, lightcurve generation is quite simple.
+
+Given a series of time points, the ephemeris of the system, the system scale and the planet star radius ratio, the position of the planet relative to the star can be calculated for each timestep.
+
+Since it is assumed that the planet is tidally locked, at each timestep the geometric grid representing the planet is populated with the appropriate fluxes from the chosen flux distribution model.
+
+Then, for each segment on the planet, it is checked whether it is currently being occulted.
+This is quickly achieved by checking for contact between the edges of the region and the edge of the star.
+If there are no contact points, and the distance from the center point to the center point of the star is greater than the stellar radius, then the segment is fully visible, and the full flux is counted, if the distance is less then the stellar radius then it is fully occulted and no flux is added.
+For cases of partial coverage, the previously described geometric integrator is used to calculate the flux that should be added.
+
+To this, the pre-calculated stellar total flux is added to give the total system flux. This is then divided by the stellar flux to give a relative lightcurve that can easily be compared to data.
 
@@
 \includegraphics[width=\textwidth]{img/huge_triangle.pdf}
-\caption{stupidly big triangle plot1}
+\caption{This triangle plot includes all the parameters that were used to fit the free limb darkening case.}
 \label{fig:big triangle}

### 2016-10-20 ms.tex
small changes

@@
 The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
-
-\citep[e.g.][]{Showman2015}
 
@@
 
+A model instance is initialised by typing
+
+\begin{Verbatim}[frame=single]
+> spider_params = spiderman.ModelParams(MODEL)
+\end{Verbatim}
+
+Where MODEL is the chosen surface brightness distribution. The model parameters are then entered, and from there, generating a lightcurve to compare to data is as simple as entering
+
+\begin{Verbatim}[frame=single]
+> spider_params.lightcurve(t)
+\end{Verbatim}
+
+Where t an array of timepoints where the model is to be evaluated.
+
 \textsc{spiderman} comes prepackaged with several plotting scripts to make visualisation of the model simple.
 
-typing the command
+Typing the command
 
 \begin{Verbatim}[frame=single]
-> spider_params.plot_planet()
+> spider_params.plot_planet(t)
 \end{Verbatim}
 
-Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date.
+Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date (t).
 If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.
@@
 
-The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.
+Figure \ref{fig:exec_time} shows the result of a performance test carried out on a single core of an Intel Core I5-3470 Processor.
+The length of time to produce a model with 1000 timepoints as a function of the number of segments of the model.
+The test shows that the execution time scales linearly with the number of segments in the model, which is expected, showing the overhead to run the model is very small.
+The precision required for typical usage can easily be reached using 16 or 25 segments, but larger numbers of segments can be used to produce better looking diagrams.
+The diagrams in this paper were generated with a 400 segment model.
 
@@
 \end{figure}
-
-\subsection{Available models}\label{sec:ttof}
 
@@
 In principle, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet, however this would require a full radiative transfer treatment of the planet.
+
+As this effect is poorly understood, we run the fit both with and without planetary limb darkening.
 
@@
 
-The only way to properly access the errors on the parameter values of interest, and test for degeneracies
+It is important to properly access the errors on the parameter values of interest, and test for degeneracies, so we run an MCMC analysis of the model fit.
+We use the \textsc{emcee}  affine invariant monte carlo implementation of \citet{emcee}
 
@@
 
+The initial parameter positions are found with a least squares minimisation approach, and the walkers
+
 For both models, the MCMC was run for 10 million steps, with the first 200,000 steps were discarded as burn in.
 
-\subsection{Results}\label{sec:results}
+\subsection{Results and discussion}\label{sec:results}
 
-In table \ref{tab:results}
+The results of both runs are presented In table \ref{tab:results}.
+There is very little difference between the fitted parameters with and without limb darkening.
+The value of $T_n$ is lower by more than $3\sigma$ in the fit with planetary limb darkening
 
@@
 \end{figure*}
-
-\subsection{Discussion}\label{sec:Discussion}
 

### 2016-10-20 ms.tex
corrected address

@@
 $^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
-$^{2}$Department of Astronomy, Harvard, America, America, America}
+$^{2}$Department of Astronomy, Harvard University, Cambridge, MA 02138, USA}
 
@@
 WASP-43b appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to a zero limb darkening.
-However, as discussed in \ref{sec:discussion}, I will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
+However, as discussed in \ref{sec:discussion}, we will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
 
@@
 It is important to properly access the errors on the parameter values of interest, and test for degeneracies, so we run an MCMC analysis of the model fit.
-We use the \textsc{emcee}  affine invariant monte carlo implementation of \citet{emcee}
+We use the \textsc{emcee}  affine invariant monte carlo implementation of \citet{Foreman-Mackey2013}
 
-During the MCMC fit I place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
+During the MCMC fit we place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
 This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.

### 2016-10-20 ms.tex
kavli version

@@
 % Keep the title short and informative.
-\title[spiderman]{\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.}
+\title[SPIDERMAN]{SPIDERMAN: an open source code to model phase curves and secondary eclipses.}
 
@@
 
-The planets are hot enough that they have appreciable infrared flux emission, with contrasts with their parents stars of order 0.1\%, making detection with current generation instruments feasible.
+General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}.
+An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
+An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.
+This effect can also be mimicked by a high eccentricity.
+\citet{Zhang2016} showed that this behaviour could be captured with a simple analytical formalism.
+
+Hot Jupiters are hot enough that they have appreciable infrared flux emission, with contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
 \citet{Deming2005} detected the infrared flux of HD\,209458b by observing the secondary transit of the planet with the MIPS instrument on \emph{Spitzer}.
@@
 Intriguingly, the phase of this sinusoidal curve was significantly offset from the time of secondary eclipse, validating earlier predictions from GCM's.
+
+There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
+$\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
+\citep{Harrington2006,Cowan2007,zellem2014}.
+
+The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
+
+WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
+The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be re-analysed here.
 
@@
 
-There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
-$\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
-\citep{Harrington2006,Cowan2007,zellem2014}.
-WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
-The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be re-analysed here.
-
-The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
-
-General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}
-
-An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
-
-An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.
-This effect can also be mimicked by a high eccentricity.
-
-\citet{Zhang2016} showed that this behaviour could be captured with a simple analytical formalism.
-
-BATMAN \citep{Kreidberg2015a}
-
-There does not currently exist an open source code for calculating secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
+BATMAN \citep{Kreidberg2015a} is a fast and accurate analytical model of exoplanet primary transits, the code is open source and publicly available.
+BATMAN serves as the inspiration for this project, as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
 
@@
 Given a series of time points, the ephemeris of the system, the system scale and the planet star radius ratio, the position of the planet relative to the star can be calculated for each timestep.
+Light time of travel effects are accounted for, with the semi-major axis as a parameter.
 
@@
 To this, the pre-calculated stellar total flux is added to give the total system flux. This is then divided by the stellar flux to give a relative lightcurve that can easily be compared to data.
+
+Note that \textsc{spiderman} does not calculate primary transits.
+To fit models to data that contain both primary and secondary eclipses, \textsc{spiderman} should be combined with another package such as BATMAN.
+The parameter naming convention and call sequence fro \textsc{spiderman} has been chosen specifically to be compatible with BATMAN for this reason.
 
@@
 \begin{Verbatim}[frame=single]
-> spider_params.plot_system()
+> spider_params.plot_system(t)
 \end{Verbatim}
@@
 The desired phase or julian date can be given as an argument.
-These plots can be very useful for visualising the physical impacts of
+These plots can be very useful for visualising the physical impacts of the chosen parameters.
 
@@
 WASP-43b appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to a zero limb darkening.
-However, as discussed in \ref{sec:discussion}, we will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
+However, as discussed in \ref{sec:results}, we will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
 
@@
 It is important to properly access the errors on the parameter values of interest, and test for degeneracies, so we run an MCMC analysis of the model fit.
-We use the \textsc{emcee}  affine invariant monte carlo implementation of \citet{Foreman-Mackey2013}
+We use the \textsc{emcee} affine invariant Monte Carlo implementation of \citet{Foreman-Mackey2013}.
 
-During the MCMC fit we place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
+The initial parameter positions are found with a least squares minimisation approach, and the 1000 walkers were placed in a tight Gaussian ball around these best fitting values.
+
+Due to the uncertainties around planetary limb darkening, we choose to run a model with limb darkening disabled, and a second where the limb darkening fit for, with minimal constraints.
+During the MCMC fit that includes planetary limb darkening, we place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
 This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
 
-The initial parameter positions are found with a least squares minimisation approach, and the walkers
+For the orbital and system parameters we use published values and errorbars as the priors.
+For the Period, inclination and $a/R_*$ we use the results of \citet{Hoyer2016}, and for $a$ the value from \citet{Hellier2011a}, The eccentricity was fixed at 0, which is well supported by the findings of \citet{Hoyer2016}.
+The stellar log g and effective temperature priors are from \citet{Gillon2012}.
 
-For both models, the MCMC was run for 10 million steps, with the first 200,000 steps were discarded as burn in.
+For both models, the MCMC was run for 10 million steps, with the first 200,000 steps discarded as burn in.
 
@@
 
-The results of both runs are presented In table \ref{tab:results}.
-There is very little difference between the fitted parameters with and without limb darkening.
-The value of $T_n$ is lower by more than $3\sigma$ in the fit with planetary limb darkening
+The best fitting model and the residuals are shown in figure \ref{fig:phase folded} as a function of planetary phase, after correction for instrument systematics.
+The data and model are also plotted as a function of time in figure \ref{fig:systematics}.
+To demonstrate the systematics model the data are plotted with and without systematics correction.
 
@@
 \end{figure}
+
+The results of both runs are presented In table \ref{tab:results}.
+There is very little difference between the fitted parameters with and without limb darkening.
+The value of $T_n$ is lower by more than $3\sigma$ in the fit with planetary limb darkening, but the other parameters in the physical model, $\Delta T$ and $\xi$ are consistent to within $2\sigma$ between the two runs.
+it is particularly worth noting how apparently unaffected $\xi$ is by the presence of limb darkening, the difference being much less than $1\sigma$.
+This makes sense, as $\xi$ effectively parametrises the asymmetry in the flux distribution, while the limb darkening is symmetrical.
+This is fortunate, as $\xi$ is the most physically interesting of the model parameter, and is directly tied to the details of heat transport in the atmosphere.
+The insensitivity of this parameter to limb darkening is important, as it shows that it can be recovered reliably even in ignorance of the vertical temperature structure of the planets atmosphere.
 
@@
 
+It is also interesting to check the correlation of this $\xi$ parameter with the other model parameters, this can be seen in the corner plot in figure \ref{fig:triangle corner sub}, which is a subset of the full diagram in figure \ref{fig:big triangle}.
+$T_s$ and $\Delta T$ are clearly correlated parameters, which is logical, as between them they determine the average temperature of the dayside, which controls the amplitude of the phase curve.
+Crucially, $\xi$ is not strongly degenerate with the other parameters.
+This indicates that the $\xi$ parameter is robust to any errors in the absolute flux level of the system, due to, for example, not modelling the instrument response curve.
+
+The visual representation of the flux maps for the non-limb darkened case can be seen in figure \ref{fig:best_fit_flux}.
+The best fitting model is displayed at 4 phases, as well as the relative error on the flux distribution.
+The error map was generated by drawing 10,000 maps from the MCMC posterior and taking the standard deviation of the fluxes in each segment.
+The offset hot-spot is significant and clearly visible.
+The underlying temperature maps, and the errors in these, are shown in figure \ref{fig:best_fit_temp}.
+
+An intriguing difference between our model fit and the previous fit by \citet{Stevenson2014} is that we are able to infer a nightside temperature, where they were only able to place upper limits.
+To demonstrate that the flux from the nightside is a real feature in the model fit, and not an abstract parameterisation of some other feature, we investigate the flux level just outside of the primary transit.
+If the nightside has indeed been significantly detected, the flux here should be significantly different to the star-only flux visible during the secondary eclipse (which is 1.0 by definition).
+Drawing 10,000 lightcurves from the parameters in the non-limb darkened MCMC posterior, we plot the median, 1 sigma and 3 sigma contours for the lightcurve in figure \ref{fig:model}.
+The flux both just before, and just after the primary transit is significantly greater than 1.0 at the 3 sigma level, indicating that there is indeed flux detected from the night side of the planet.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/model.pdf}
+\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
+\label{fig:model}
+\end{center}
+\end{figure}
+
+Repeating this test with the limb darkened fit does not find significant night side flux, which casts doubt on the significance of this detection.
+The difference between our two model results and the results of \citet{Stevenson2014} may be due to the detrending process, or in the sample of data used in the final fit, and requires more investigation.
+
+Surprisingly, the model fit including limb darkening actually shows a significant preference for \emph{limb brightened} profiles.
+To visualise this, 10,000 limb profiles are drawn from the posterior, and their one and three sigma confidence intervals plotted in figure \ref{fig:limb brighten}.
+The profiles are clearly limb brightened, which is unexpected, since previous work has shown that WASP-43b has a near isothermal profile which would inhibit limb brightening or limb darkening \citep{Stevenson2014}.
+However, despite this unexpected result, as previously discussed, there is no significant difference to the physical model fit of \citep{Zhang2016}, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
+\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
+\label{fig:limb brighten}
+\end{center}
+\end{figure}
+
 \begin{center}
 \begin{table*}{
-\caption{This is my caption}
+\caption{The full results from the MCMC fit both with and without planetary limb darkening included.}
 \begin{center}
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
-\caption{left: right: the constraints on the brightness distribution, for the model where the planetary limb darkening was switched off.}
-\label{fig:best_fit_flux}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
-\caption{The underlying temperature distributions generated by the zhang model.}
-\label{fig:best_fit_temp}
-\end{center}
-\end{figure*}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/model.pdf}
-\caption{the uncertainty on the model from the MCMC fit. There is a greater than 3 sigma detection of night-side flux.}
-\label{fig:model}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
-\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
-\label{fig:limb brighten}
-\end{center}
-\end{figure}
-
 \section{Future work}\label{sec:future work}
@@
 \begin{itemize}
-\item More thermal brightness distributions, such as an "orange segments" model and a simple parametrised hotspot which can be offset in latitude and longitude
+\item More thermal brightness distributions, such as an ``orange segments'' model and a simple parametrised hotspot which can be offset in latitude and longitude
 \item Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{img/systematics.pdf}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
+\caption{left: The best fitting flux distribution for the model where the planetary limb darkening was switched off at 4 phases, from top left clockwise the phases are 0, 0.25, 0.75 and 0.5.
+right: The respective constraints on the brightness distribution}
+\label{fig:best_fit_flux}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+\caption{The underlying temperature distributions generated by the zhang model.}
+\label{fig:best_fit_temp}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{img/systematics.pdf}
 \caption{Top: raw data from HST, the systematic components are all visible.
@@
 
-The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonothan Fortney and Pascale Geurard.
+The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonothan Fortney and Pascale Garaud.
 

### 2016-10-24 ms.tex
hello

@@
 
-Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints of the physics of the atmosphere, such as the ratio between advective and radiative timescales.
+Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints on the physics of heat transport in the atmosphere, such as the ratio between advective and radiative timescales.
 
@@
 
-There are a small number of different general "cases" for the numbers of triangles and segments that must be used, that can be selected based on the number and types of "collision points" between the planet region and the stellar circle.
+There are a small number of different general ``cases" for the numbers of triangles and segments that must be used, that can be selected based on the number and types of ``collision points" between the planet region and the stellar circle.
 Therefore, the first step for calculating the occulted area for each segment of the planet is to calculate these collision points.
@@
 Finding the collision points between an arc or a line and a circle (the star), if any exist, are trivial and fast to calculate.
-The code then classifies the geometric "case" of the collision based on the number of collision points on the 4 boundary sides.
+The code then classifies the geometric ``case" of the collision based on the number of collision points on the 4 boundary sides.
 
@@
 The $\xi$ parameter is perhaps the most interesting, as it effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere.
-The effects of this can be seen in \ref{fig:ex_lcs}, where
+The effects of this can be seen in \ref{fig:ex_lcs}, where both the position of the maxima of the phase curve, and the shape of the ingress and egress of the secondary eclipse are clearly effected by this asymmetry.
 
@@
 Due to the low earth orbit of Hubble, each complete orbit lasts 95 minutes, and for approximately half of this time the target will be unobservable due to being behind the Earth.
-For this reason, a complete exoplanet transit can not be observed with one "visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.
+For this reason, a complete exoplanet transit can not be observed with one ``visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.
 
@@
 
-The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonothan Fortney and Pascale Garaud.
+The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonathan Fortney and Pascale Garaud.
 

### 2017-07-12 ms.tex
local

@@
 % out the following line
-\usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 Using a geometrical algorithm, the code solves exactly the area of sections of the disc of the planet that are occulted by the star.
-The code is written in C and optimised to run extremely quickly, with no loss in precision.
-Approximately 1000 models can be generated per second with typical parameters.
+The code is written in C and optimised to run quickly, with no loss in precision.
+Approximately 1000 models can be generated per second with typical parameters, making Markov Chain Monte Carlo analyses practiable.
 
-Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints on the physics of heat transport in the atmosphere, such as the ratio between advective and radiative timescales.
+Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b.
+The model provides a good fit to the data, however, the best fitting model significantly overpredicts the temperature of the night-side.
+We speculate that this could be due to the presence of clouds on the night side of the planet.
+
+We test statistically for variation of the map parameters as a function of wavelength and find no statistically strong confirmation of a dependence.
 
@@
 
-Secondary eclipses and phase curves can give direct insight into the thermal transport processes, and vertical structure of an exoplanet atmosphere.
+Secondary eclipses and phase curves can give direct insight into the thermal transport processes, and when wavelength resolved also give information on the vertical structure of an exoplanet atmosphere.
 
@@
 An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
+The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection.
+
 An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.

### 2017-07-16 ms.tex
updated

@@
 An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
-The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection.
+The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection (citation).
 
-An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be offset from the time of secondary transit by a measurable amount.
-This effect can also be mimicked by a high eccentricity.
-\citet{Zhang2016} showed that this behaviour could be captured with a simple analytical formalism.
+An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be delayed from the time of secondary transit by a measurable amount.
+This effect can also be mimicked by a high eccentricity \citep{J.deWit2012a} (is this the right citation?).
 
-Hot Jupiters are hot enough that they have appreciable infrared flux emission, with contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
+Hot Jupiters, with temperatures of order 1000 K are hot enough that they have appreciable infrared flux emission, affording contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
 \citet{Deming2005} detected the infrared flux of HD\,209458b by observing the secondary transit of the planet with the MIPS instrument on \emph{Spitzer}.
@@
 There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
+Hot Jupiters like HD\,189733b with, relatively temperatures have highly significant hotspot offsets and efficient day-night redistribution (cite examples other than HD 189).
 $\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
@@
 
+This behaviour has been anticipated in models (cite thad komacek?)
+
 The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
 
-WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
+/%WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
 The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be re-analysed here.
@@
 
-BATMAN \citep{Kreidberg2015a} is a fast and accurate analytical model of exoplanet primary transits, the code is open source and publicly available.
-BATMAN serves as the inspiration for this project, as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
+POTENTIAL OF JWST
+
+\textsc{batman} \citep{Kreidberg2015a} is a fast and accurate analytical model of exoplanet primary transits, the code is open source and publicly available.
+\textsc{batman} serves as the inspiration for this project, as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
+
+In this paper we first describe the model, and provide a brief overview of the use of the code, and then an example of use on the hot Jupiter WASP-43b.
 
@@
 
-\textsc{spiderman} has several different ways to model the brightness distribution, including a simple uniform distribution, and a non-informative model based on spherical harmonics (displayed visually in figure \ref{fig:harmonics}).
-However, the most interesting application is the physical model developed by \citet{Zhang2016}.
+\textsc{spiderman} has been written in a modular way, so that users will be able to choose from a variety of models to fit to their data, or provide their own.
+
+The currently availible models range from fully non-informative to basic physical models, and also utilities to allow the results of forward models to be quickly converted into phase curves and eclipses.
+
+\textsc{spiderman} projects this temperature map onto the visible sphere of the planet, meaning it is used directly to calculate the secondary eclipse and phase curve.
+
+\subsubsection{Spherical harmonics}
+
+displayed visually in figure \ref{fig:harmonics}
+
+\subsubsection{Hotspot models}
+
+\subsubsection{Physical model}
+
+\citet{Zhang2016}.
 This model was developed as part of a simple analytical framework to describe the broad trends within complex GCM's, and does a remarkably good job of replicating the temperature distributions of GCM's with only three free parameters.
@@
 
-\textsc{spiderman} projects this temperature map onto the visible sphere of the planet, meaning it is used directly to calculate the secondary eclipse and phase curve.
 This is the first time a physical model of atmosphere circulation has been used to directly fit to data.
@@
 \end{figure}
+
+\subsubsection{Forward model}
+
+\textsc{spiderman} also has the capability to quickly calculate a phase curve and secondary eclipse from a pre-calculated forward model.
+The code can read in a grid of either temperatures or brightnesses, in longitude and latitude, and will use a two dimensional bicubic interpolation within this grid to assign brightnesses to the grid points at each time-step.
+Continuity is assumed east-west and across the poles to minimise edge effects.
+This is significantly slower than the other models due to the interpolation scheme, but it is assumed that the generation of the forward model is by far the biggest bottle-neck in the calculation, so in this instance speed is not the priority.
+This mode is intended to be used in particular for modelling eclipse mapping observations from 3D GCM calculations, either for comparison to data or to test analytical theories.
+
+((figure of 2D GCM results from Viven - would need permission))
 
@@
 At present \textsc{spiderman} only interpolates in temperature, and picks the closest surface gravity and metalicity in the table, which will lead to small errors in the fluxes.
-Future versions of the code will interpolate in these values as well, allowing an MCMC to better model the uncertainty on the stellar surface brightness.
+Future releases of the code will interpolate in these values as well, allowing an MCMC to better model the uncertainty on the stellar surface brightness.
 
@@
 Given a series of time points, the ephemeris of the system, the system scale and the planet star radius ratio, the position of the planet relative to the star can be calculated for each timestep.
-Light time of travel effects are accounted for, with the semi-major axis as a parameter.
+Light time of travel effects are accounted for, with the semi-major axis in physical units as a parameter.
 
@@
 To fit models to data that contain both primary and secondary eclipses, \textsc{spiderman} should be combined with another package such as BATMAN.
-The parameter naming convention and call sequence fro \textsc{spiderman} has been chosen specifically to be compatible with BATMAN for this reason.
+The parameter naming convention and call sequence from \textsc{spiderman} has been chosen to be compatible with BATMAN for this reason.
 
@@
 
-Or, to access the bleeding-edge development version from github:
+Or, to access the development version from github:
 
@@
 Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy.
-As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.\\
+As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
 
-Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in \citet{Gibson2012a}, this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
+For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well ((wakeford reff)).
+Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however there might be concerns that if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
+
+An alternative, powerful technique which does not make assumptions about the form of the systematics is Gaussian Processes \citep[e.g.][]{Gibson2012a}.
+((Find a more recent reference with regards to JWST, or the one comparing sytematis models on HST and spitzer))
+%Future analysis of this dataset could use a Gaussian process noise model instead of the parametrised one featured here, as used in \citet{Gibson2012a}, this could provide further confidence in the results, as the added flexibility of the GP model and the explicit fit for the timescale of the features would allow the degeneracy to be explored with fewer explicit hyper-parameters.
+
+An important early result from JWST will be a characterisation of the systematics, particularly for MIRI, as this will have significant consquencies for the practicality of phase curve and eclipse mapping observations with JWST.
 
@@
 
+As a test of the physical nature of this nightside flux, we repeat the fit with an additional model parameter which allows \emph{planetary} limb darkening or brightening.
+
 Repeating this test with the limb darkened fit does not find significant night side flux, which casts doubt on the significance of this detection.
-The difference between our two model results and the results of \citet{Stevenson2014} may be due to the detrending process, or in the sample of data used in the final fit, and requires more investigation.
 
-Surprisingly, the model fit including limb darkening actually shows a significant preference for \emph{limb brightened} profiles.
-To visualise this, 10,000 limb profiles are drawn from the posterior, and their one and three sigma confidence intervals plotted in figure \ref{fig:limb brighten}.
-The profiles are clearly limb brightened, which is unexpected, since previous work has shown that WASP-43b has a near isothermal profile which would inhibit limb brightening or limb darkening \citep{Stevenson2014}.
+inhibit limb brightening or limb darkening \citep{Stevenson2014}.
 However, despite this unexpected result, as previously discussed, there is no significant difference to the physical model fit of \citep{Zhang2016}, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
-\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
-\label{fig:limb brighten}
-\end{center}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=\columnwidth]{img/ld_prof.pdf}
+%\caption{The 1 sigma and 3 sigma contours for the Radial intensity profile of the planet, indicating that the fit has a significant preference for limb brightened profiles }
+%\label{fig:limb brighten}
+%\end{center}
+%\end{figure}
 
@@
 
-\section{Future work}\label{sec:future work}
+\section{Conclusions}\label{sec:conclusions}
 
-\textsc{spiderman} is still under development, and there are a number of features that are planned to be implemented:
+In this paper we have introduced \textsc{spiderman}, an open source code for modelling phase curves and secondary eclipses with arbitrary brightness distributions.
+The code is modular and able to use a variety of different brightness distributions.
 
-\begin{itemize}
-\item More thermal brightness distributions, such as an ``orange segments'' model and a simple parametrised hotspot which can be offset in latitude and longitude
-\item Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
-\item Allow calculation of multiple spectral channels simultaneously, with linked system parameters.
-\item Include instrument response in calculating flux ratios
-\item Better treatment of errors in the spectral energy distribution of the star - include errors in log-g and Metalicity
-\end{itemize}
+The C based algorithm analytically calculates the area occulted of radial segments on the planets surface, and is designed to run rapidly to enable statistical techniques such as MCMCs to run quickly.
 
-In regards to the re-analysis of WASP-43bs phase curve, future analysis will focus on:
+We demonstrate the use of \textsc{spiderman} by applying the code to the case of WASP-43b.
+We use a physically motivated analytical model presented by \citet{zhang2016} which captures the major features of exoplanet phase curves.
+We find that the model provides a good fit to the data, but overpredicts the nightside flux compared to non-informative models.
+We hypothesise that this may be due to the presence of clouds on the planets nightside.
 
-\begin{itemize}
-\item Confirming the detected flux on the nightside is a real feature and not an artefact
-\item Further test for degeneracies between HST systematics and the physical model of the phase curve, in particular the combination of visit long slope and breathing modes.
+As the exoplanet community prepares for a wealth of high precision phase curves and eclipses from new facilities such as TESS and JWST, we release \textsc{spiderman} as an easy to use software package that will enable robust analysis of these high precision data.
+
+%\section{Future work}\label{sec:future work}
+
+%\textsc{spiderman} is still under development, and there are a number of features that are planned to be implemented:
+
+%\begin{itemize}
+%\item More thermal brightness distributions, such as an ``orange segments'' model and a simple parametrised hotspot which can be offset in latitude and longitude
+%\item Implement \emph{reflected} light phase curves and secondary eclipses, through adding appropriate brightness distributions like Lambertian reflectors and patchy clouds.
+%\item Allow calculation of multiple spectral channels simultaneously, with linked system parameters.
+%\item Include instrument response in calculating flux ratios
+%\item Better treatment of errors in the spectral energy distribution of the star - include errors in log-g and Metalicity
+%\end{itemize}
+
+%In regards to the re-analysis of WASP-43bs phase curve, future analysis will focus on:
+
+%\begin{itemize}
+%\item Confirming the detected flux on the nightside is a real feature and not an artefact
+%\item Further test for degeneracies between HST systematics and the physical model of the phase curve, in particular the combination of visit long slope and breathing modes.
 This could be accomplished by a Gaussian process analysis.
-\item Perform recovery with a non-informative model, such as spherical harmonics, and see if the recovered brightness or temperature maps are the same as recovered through physical models.
-\item Investigating the apparent preference for limb brightened profiles in the model fit.
+%\item Perform recovery with a non-informative model, such as spherical harmonics, and see if the recovered brightness or temperature maps are the same as recovered through physical models.
+%\item Investigating the apparent preference for limb brightened profiles in the model fit.
 This is characteristic of a temperature inversion, but since there is no evidence for this in other data on WASP-43b it may be more likely that it indicates a weakness of the model.
-\item Making wavelength resolved maps.
+%\item Making wavelength resolved maps.
 This will allow spectra as a function of latitude and longitude to be created.
 The wavelength also functions as a proxy for height in a planetary atmosphere, so the map will effectively be three dimensional.
-\item Investigate correlations between spectrally resolved bins and consider the impact of simultaneous fits.
-\end{itemize}
+%\item Investigate correlations between spectrally resolved bins and consider the impact of simultaneous fits.
+%\end{itemize}
 

### 2017-07-16 ms.tex
overleaf

@@
 
-The model is designed so that an arbitrary brightness distribution can be used, and that the resulting phase curve and secondary eclipse lightcurves can be calculated rapidly and accurately.
+In order to accurately calculate both the phase curve and secondary eclipse the code must integrate over the portion of the planet that is facing the observer and is not occulted by the star at each time-step.
+In order to be general use and ``model agnostic'' the integrator cannot assume any specific properties or symmetries in the brightness distribution.
+This can be done numerically, by sampling a grid of points on the planets surface and summing those that are visible, but to achieve high precisions a large number of points would need to be sampled, which would be slow and computationally inefficient.
 
-The visible disc of the planet is divided into a series of annuli, and then these in turn are separated in theta.
+Instead, \textsc{spiderman} uses an analytical integration scheme where the planet is divided into a relatively small number of regions, and the area of each region that is not occulted by the star is calculated exactly through geometry.
+The average surface brightness of each region is determined by the chosen model and multiplied by the visible area to get the total flux.
+
+\textsc{spiderman} uses a radial co-ordinate system centered on the visible hemisphere of the planet.
+The planet is defined to have a radius of 1 and the visible disc of the planet is divided into a series of annuli, and then these in turn are separated in theta, see the schematic in figure \ref{fig:schematic}.
 The number of segments in each annuli are chosen so that the area of every sector is the same.
-This results in 1 circular segment in the center, then 3 regions in the second annuli See the schematic in figure \ref{fig:schematic}.
-The planet is defined to have a radius of 1.
-Other grid schemes could be implemented in future versions, for example, if it is decided that the information content is higher in some parts of the planet than others then the grid could be made finer in these regions.
+This results in 1 circular segment in the center, then 3 regions in the second annuli and 5 in the third - with the number of segment in the nth annuli being 2n - 1.
+Using this scheme, dividing the planet n times radially results in a total of n$^2$ integration elements.
 
-In practice, it is found that dividing the planet into 5 radially (25 total sectors) gives results within a few percent of higher density grids, and is significantly faster to run.
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
+		\caption{Schematic representation of the planet grid. All sectors are equal area.}
+		\label{fig:schematic}
+	\end{center}
+\end{figure}
 
@@
 
-The advantage of this geometric approach is that the planet can be described by a small number of regions with no loss in numerical precision, enabling eclipses and phase curves to be calculated extremely rapidly.
+Numerical errors can be introduced by this approach if the brightness distribution changes significantly faster than the area elements, but the size of the elements can be adjusted as necessary by the user, at the cost of computation time.
+In practice, we found that dividing the planet into 5 radially (giving 25 total elements) gave sufficient precision for the smoothly varying brightness profile in our WASP-43b test case, and increasing the mesh density beyond this point did not change the results.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.8\columnwidth]{img/frame1.pdf}
-\caption{Schematic representation of the planet grid. All sectors are equal area.}
-\label{fig:schematic}
-\end{center}
-\end{figure}
+Other grid schemes could be defined, for example, if it is decided that the information content is higher in some parts of the planet than others then the grid could be made finer in these regions.
 
@@
 
-To test that the integrator is working correctly, a simple test was conducted.
-Assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have zero impact on the final light-curve.
-With a large number of segments and time points, all geometrical cases will be met, and it will quickly become obvious if there is a mistake in how the areas have been calculated.
+Assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have no impact on the final light-curve.
 
-We compare the case of a single segment model, i.e., a circle, for which there is a single analytical solution to the area blocked by another circle, to one with 400 segments.
+To test that the integrator is performing correctly we compare the case of a single segment model, i.e., a circle, for which there is a single analytical solution to the area blocked by another circle, to one with 400 segments.
 In both cases the planet is assumed to have a total luminosity that is 1\% that of the star's.
@@
 
-\subsection{The temperature model}\label{sec:temp model}
+\subsection{The brightness models}\label{sec:temp model}
 
@@
 
-\subsection{Temperature to fluxes}\label{sec:ttof}
+\subsubsection{Converting temperature to fluxes}\label{sec:ttof}
 
-Some physical models, such as the one adapted from \citep{Zhang2016} are defined in terms of temperature, where of course the observable that is being fit for is the emitted flux.
-Therefore, it is necessary to convert from one to the other.
+Some physical models, such as the one adapted from \citep{Zhang2016}, are defined in terms of temperature, so \textsc{spiderman} must convert that to a flux.
+To do so we make the assumption that the temperature corresponds to the \emph{brightness temperature} of the planet's photosphere.
+This will be valid for band passes that are narrower than strong molecular bands in the spectrum, such as water or carbon monoxide, but will not hold over wide band-passes.
 
-If we make the assumption that the temperature distribution maps to the \emph{brightness temperature} distribution, then we can recover these fluxes.
-This will be valid for band passes that are narrower than potentially strong molecular bands in the spectrum, such as water or carbon monoxide, but this assumption may introduce systematic errors into very wide band-passes.
-
-We treat the planet as a ideal blackbody, which is clearly a simplification.
-For the planet the brightness temperature, or the temperature of a perfect blackbody emitting the same amount of flux within a bandpass, is a widely used convention, and is the direct observable.
-
-The total flux emitted by a blackbody has a trivial solution, however, \textsc{spiderman} is intended to model the observations of real instuments, which will of course only sample a very small sample of the electromagnetic spectrum.
-There is not an analytical expression for the total amount of flux emitted by a blackbody within an arbitrary wavelength band.
-
-An additional factor that is not currently considered by the model but will be featured in future releases of the code is to also include the ability for the user to define instrument response functions as a function of wavelength.
+There is not an analytical expression for the total amount of flux emitted by a blackbody between two arbitrary wavelengths, so \textsc{spiderman} calculates this value numerically.
+A grid of blackbody curves multiplied by the instrument response is pre-calculated as a function of temperature, and the flux in the chosen wavelength region is summed numerically.
+\textsc{spiderman} then linearly interpolates on this grid when assigning fluxes to the planet integration regions based on their temperature.
 
@@
 
-Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, lightcurves can comfortably be fit by very unphysical planet and star fluxes, so long as the ratio between them is of the right order.
-There will clearly be an enormous degeneracy between the planet and star brightness.
+Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, there will clearly be an exact degeneracy between the planet and star brightness.
+In order to recover physical parameters of the planet, such as temperature, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.
+These constraints only need to be on flux as a function of surface area, i.e., on the specific intensity of the system components, and on their radius ratio, not on their total luminosity or radii.
 
-In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.
-Somewhat counter-intuitively, these constraints only need to be on flux \emph{as a function of surface area}, i.e., on the specific intensity of the system components, and on their radius ratio, not on their total luminosity or radii.
-
-To see that this is indeed the case, consider a situation where the radii of both the planet and the star have both been underestimated by a factor of 2, but their surface intensities are unchanged, such that the total luminosity will have been underestimated by a factor of 4.
+%To see that this is indeed the case, consider a situation where the radii of both the planet and the star have both been underestimated by a factor of 2, but their surface intensities are unchanged, such that the total luminosity will have been underestimated by a factor of 4.
 The secondary eclipse depth and phase curve amplitude both scale as $(R_p / R_*)^2$, so are unchanged.
@@
 
-For the star however, we can do better than this.
-From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, which allow the observed stellar spectrum to be matched to a model spectra with physical units.
-This fixes the flux scale of the system, allowing useful constraints to be placed on the absolute flux level of the planet by extension.
+$(R_p / R_*)^2$ is well constrained from primary transits - the small variation as a function of wavelength is of little importance.
+There are usually good measurements of the effective temperature of the star from spectroscopy and stellar modelling.
+These additional parameters fix the flux scale of the system, allowing useful constraints to be placed on the absolute surface flux and brightness temperature of the planet.
 
 \textsc{spiderman} models the stellar spectrum using a grid of PHOENIX stellar atmospheres calculated by \citet{Husser2013}.
-Using the user provided wavelength bandpass, \textsc{spiderman} calculates the total flux in this bandpass for the available models as a function of effective temperature, it then interpolates using a simple spline fit to calculate the flux for the effective temperature of the star.
-Internally, this is multiplied by the stellar radius to get an absolute flux level for the system.
-
-At present \textsc{spiderman} only interpolates in temperature, and picks the closest surface gravity and metalicity in the table, which will lead to small errors in the fluxes.
-Future releases of the code will interpolate in these values as well, allowing an MCMC to better model the uncertainty on the stellar surface brightness.
+Using the user provided wavelength bandpass and instrument response, \textsc{spiderman} calculates the total observed flux for the available models as a function of effective temperature, it then interpolates on this grid using a spline.
 
@@
 
-The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planets phase curve, so there is potential for serious degeneracies between the systematics and the physical model.
+The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planet's phase curve, so there is potential for serious degeneracies between the systematics and the physical model.
 
@@
 This is fortunate, as $\xi$ is the most physically interesting of the model parameter, and is directly tied to the details of heat transport in the atmosphere.
-The insensitivity of this parameter to limb darkening is important, as it shows that it can be recovered reliably even in ignorance of the vertical temperature structure of the planets atmosphere.
+The insensitivity of this parameter to limb darkening is important, as it shows that it can be recovered reliably even in ignorance of the vertical temperature structure of the planet's atmosphere.
 
@@
 
-The C based algorithm analytically calculates the area occulted of radial segments on the planets surface, and is designed to run rapidly to enable statistical techniques such as MCMCs to run quickly.
+The C based algorithm analytically calculates the area occulted of radial segments on the planet's surface, and is designed to run rapidly to enable statistical techniques such as MCMCs to run quickly.
 
@@
 We find that the model provides a good fit to the data, but overpredicts the nightside flux compared to non-informative models.
-We hypothesise that this may be due to the presence of clouds on the planets nightside.
+We hypothesise that this may be due to the presence of clouds on the planet's nightside.
 

### 2017-07-16 get_bib.sh
overleaf

@@ -1,1 +1,1 @@
-cp /home/astro/phrmat/Documents/BibTeX/Papers-SPIDERMAN.bib bibliography.bib
+cp ../../BibTeX/Papers-SPIDERMAN.bib bibliography.bib

### 2017-07-16 get_bib.sh
overleaf

@@ -1,1 +1,0 @@
-cp ../../BibTeX/Papers-SPIDERMAN.bib bibliography.bib

### 2017-07-16 ms.tex
Update on Overleaf.
new plot

@@
 
-For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well ((wakeford reff)).
+For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well \citet{Wakeford2016}.
 Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however there might be concerns that if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
@@
 
+\begin{table}{
+			\caption{The full results from the MCMC fit both with and without planetary limb darkening included.}
+			\begin{center}
+				\begin{tabular}{c c}
+					\hline
+					\hline
+					Central wavelength &   log10(xi)  \\
+					(microns) & \\
+					\hline
+1.1425 & -0.32 $\pm$ 0.27 \\
+1.1775 & -0.51 $\pm$ 0.32 \\
+1.2125 & -0.00 $\pm$ 0.18 \\
+1.2475 & -0.20 $\pm$ 0.19 \\
+1.2825 & -0.74 $\pm$ 0.39 \\
+1.3175 & -0.32 $\pm$ 0.19 \\
+1.3525 & -0.82 $\pm$ 0.62 \\
+1.3875 & -0.07 $\pm$ 0.20 \\
+1.4225 & -0.09 $\pm$ 0.34 \\
+1.4575 & -0.71 $\pm$ 0.31 \\
+1.4925 & -0.42 $\pm$ 0.17 \\
+1.5275 & -0.76 $\pm$ 0.37 \\
+1.5625 & -0.43 $\pm$ 0.14 \\
+1.5975 & -0.66 $\pm$ 0.25 \\
+1.6325 & -0.59 $\pm$ 0.19 \\
+\end{tabular}
+\end{center}
+\label{tab:results}
+}
+\end{table}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=\columnwidth]{img/all_models.pdf}
+		\caption{This alright fit to Xi as a function of wavelength. blue: flat line, green: gradient function, orange: step function}
+		\label{fig:best_fit_flux}
+	\end{center}
+\end{figure}
+
+The flat model gave a value of -0.36 - note that this is a good match to the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF
+
+The best fitting gradient model had values -0.8606214   0.84938152 and gave a chi2 of 8.8 (RCHI2 0.67) with 13 DOF
+
+The best fitting model was the step function model with a dividing wavelength of 1.4225 microns, and step values of -0.5242412 -0.2149221. This gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.
+
+While we find that there is weak evidence for a trend with wavelength in the data, the flat line model provides a satisfactory fit to the data.
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-07-17 ms.tex
new plot

@@
 
-\subsection{Integrator design}\label{sec:integrator}
+\subsection{Analytical integrator}\label{sec:integrator}
 
@@
 
-\subsection{Integrator validation}\label{sec:numerical}
-
-Assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have no impact on the final light-curve.
+We performed a simple validation check to demonstrate that the integrator is working correctlyl.
+assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have no impact on the final light-curve.
 
@@
 \subsubsection{Hotspot models}
+
+The simplest physical model that one construct.
+
+These models could also be used to represent the reflection of light due to clouds in optical phase curves. ((citations to K2 stuff, armstrong))
 
@@
 It was generated with the spiderman.plot\_system() command.
-The image of the star is purely aesthetic, and does not contain any model detail.}
+The image of the star is purely aesthetic.}
 \label{fig:plot_system}
@@
 The systematics model we use to fit WASP-43 is the same that was used in the previous treatment \citep{Stevenson2014}.
+There are three components to the systematics model, the scan direction offset, ``hook effect'' and visit long slopes.
 
-In brief, there are three components to the systematics model:
-\subsection*{1.) Scan direction offset}
-
-There is an offset in the recorded flux depending on which way the the ccd was scanning during the readout, in one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the offset.
+The scan direction offset is depends on which way the the ccd was scanning during the readout, in one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the offset.
 This leads to a very repeatable offset in the fluxes between the two scan directions, which can be captured with a single parameter \emph{scale}
-
-\subsection*{2.) Orbit long ``hook effect''}
 
@@
 This exponential ramp has a different shape during the first orbit of a visit, so the $\delta_{fo}$ function takes a value of 1 if the orbit is the first, and 0 at all other times.
-
 The exponential hook shape is believed to be related to charge trapping, and is a characteristic and repeatable feature across orbits, so these parameters are fit simultaneously over visits.
-
-\subsection*{3.) Visit long slope. }
 
@@
 
-The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planet's phase curve, so there is potential for serious degeneracies between the systematics and the physical model.
+The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planet's phase curve, so there is potential for degeneracies between the systematics and physical models.
 
-Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy.
-As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.
+Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which serves to alleviate the degeneracy.
 
@@
 
-It is important to properly access the errors on the parameter values of interest, and test for degeneracies, so we run an MCMC analysis of the model fit.
+In order to properly access the errors on the parameter values of interest, and test for degeneracies with the systematics model, we perform an MCMC analysis.
 We use the \textsc{emcee} affine invariant Monte Carlo implementation of \citet{Foreman-Mackey2013}.
 
-The initial parameter positions are found with a least squares minimisation approach, and the 1000 walkers were placed in a tight Gaussian ball around these best fitting values.
+The initial parameter positions are found with a least squares minimisation approach, and the 1000 walkers were initialised around these best fitting values.
 
-Due to the uncertainties around planetary limb darkening, we choose to run a model with limb darkening disabled, and a second where the limb darkening fit for, with minimal constraints.
-During the MCMC fit that includes planetary limb darkening, we place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
-This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no non-physically flexible profiles.
+For the orbital and system parameters we use published values and errorbars as priors.
+For the Period, inclination and $a/R_*$ we use the results of \citet{Hoyer2016}, and for $a$ the value from \citet{Hellier2011a}, The eccentricity was fixed at 0, which is supported by the findings of \citet{Hoyer2016}.
+The stellar log g and effective temperature priors are from \citet{Gillon2012}.
 
-For the orbital and system parameters we use published values and errorbars as the priors.
-For the Period, inclination and $a/R_*$ we use the results of \citet{Hoyer2016}, and for $a$ the value from \citet{Hellier2011a}, The eccentricity was fixed at 0, which is well supported by the findings of \citet{Hoyer2016}.
-The stellar log g and effective temperature priors are from \citet{Gillon2012}.
+To test for the potential impact of \emph{planetary} limb darkening, we ran a second MCMC with this effect modelled by a simple quadratic limb darking law.
+We place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
+This results in profiles that are either flat, wholly limb darkened or wholly limb brightened, with no overly flexible profiles.
 
@@
 \includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
-\caption{A section of the larger corner plot in figure \ref{fig:big triangle}.
+\caption{A section of the corner plot focusing on the key model parameters.
 The parameters for the Zhang model fit are loosely correlated.
@@
 
-It is also interesting to check the correlation of this $\xi$ parameter with the other model parameters, this can be seen in the corner plot in figure \ref{fig:triangle corner sub}, which is a subset of the full diagram in figure \ref{fig:big triangle}.
+It is also interesting to check the correlation of this $\xi$ parameter with the other model parameters, this can be seen in the corner plot in figure \ref{fig:triangle corner sub}.
 $T_s$ and $\Delta T$ are clearly correlated parameters, which is logical, as between them they determine the average temperature of the dayside, which controls the amplitude of the phase curve.
@@
 \begin{table}{
-			\caption{The full results from the MCMC fit both with and without planetary limb darkening included.}
+			\caption{Fits to the spectrally resolved data}
 			\begin{center}
@@
 \end{center}
-\label{tab:results}
+\label{tab:specresults}
 }
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
-\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
-\caption{The underlying temperature distributions generated by the zhang model.}
-\label{fig:best_fit_temp}
-\end{center}
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+%\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+%\caption{The underlying temperature distributions generated by the zhang model.}
+%\label{fig:best_fit_temp}
+%\end{center}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{img/huge_triangle.pdf}
-\caption{This triangle plot includes all the parameters that were used to fit the free limb darkening case.}
-\label{fig:big triangle}
-\end{center}
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=\textwidth]{img/huge_triangle.pdf}
+%\caption{This triangle plot includes all the parameters that were used to fit the free limb darkening case.}
+%\label{fig:big triangle}
+%\end{center}
+%\end{figure*}
 

### 2017-07-19 ms.tex
overleaf

@@
 The code is written in C and optimised to run quickly, with no loss in precision.
-Approximately 1000 models can be generated per second with typical parameters, making Markov Chain Monte Carlo analyses practiable.
+Approximately 1000 models can be generated per second with typical parameters, making Markov Chain Monte Carlo analyses practicable.
 
 Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b.
-The model provides a good fit to the data, however, the best fitting model significantly overpredicts the temperature of the night-side.
+The model provides a good fit to the data, however, the best fitting model overpredicts the temperature of the night-side.
 We speculate that this could be due to the presence of clouds on the night side of the planet.
 
-We test statistically for variation of the map parameters as a function of wavelength and find no statistically strong confirmation of a dependence.
+We test statistically for variation of the map parameters as a function of wavelength and find no statistically strong correlations.
 
@@
 
-displayed visually in figure \ref{fig:harmonics}
+A completely non-physics dependent model is a sum of spherical harmonics. This has been used before by ((cite)) an example generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}
 
@@
 
-The simplest physical model that one construct.
+The simplest physically model that one construct involve defining a bulk planetary temperature or flux, and then a "Hotspot" where the contrast and offset from the substellar point in longitude and latitude are model parameters.
+Models where the day and the night side have different fluxes are a subset of these models.
 
@@
 
-\textsc{spiderman} is an open source project and is being actively developed on github.
-The code is available on PyPi, and the latest stable version can easily by installed by simply running the command
+\textsc{spiderman} is an open source project and is being actively developed on github. The code is available on PyPi and github at \url{https://github.com/tomlouden/spiderman}.
 
-\begin{Verbatim}[frame=single]
-> pip install spiderman-package
-\end{Verbatim}
+%\begin{Verbatim}[frame=single]
+%> pip install spiderman-package
+%\end{Verbatim}
 
-Or, to access the development version from github:
+%Or, to access the development version from github:
 
-\begin{Verbatim}[frame=single]
-> git clone https://github.com/tomlouden/SPIDERMAN
-> cd SPIDERMAN
-> sudo python setup.py install
-\end{Verbatim}
+%\begin{Verbatim}[frame=single]
+%> git clone https://github.com/tomlouden/SPIDERMAN
+%> cd SPIDERMAN
+%> sudo python setup.py install
+%\end{Verbatim}
 
-Full installation instructions and other information are available in the documentation, at \url{http://spiderman.readthedocs.io}
+Installation instructions and documentation are available at \url{http://spiderman.readthedocs.io}
 
-A model instance is initialised by typing
+%A model instance is initialised by typing
 
-\begin{Verbatim}[frame=single]
-> spider_params = spiderman.ModelParams(MODEL)
-\end{Verbatim}
+%\begin{Verbatim}[frame=single]
+%> spider_params = spiderman.ModelParams(MODEL)
+%\end{Verbatim}
 
-Where MODEL is the chosen surface brightness distribution. The model parameters are then entered, and from there, generating a lightcurve to compare to data is as simple as entering
+%Where MODEL is the chosen surface brightness distribution. The model parameters are then entered, and from there, generating a lightcurve to compare to data is as simple as entering
 
-\begin{Verbatim}[frame=single]
-> spider_params.lightcurve(t)
-\end{Verbatim}
+%\begin{Verbatim}[frame=single]
+%> spider_params.lightcurve(t)
+%\end{Verbatim}
 
-Where t an array of timepoints where the model is to be evaluated.
+%Where t an array of timepoints where the model is to be evaluated.
 
-\textsc{spiderman} comes prepackaged with several plotting scripts to make visualisation of the model simple.
+%\textsc{spiderman} comes prepackaged with several plotting scripts to make visualisation of the model simple.
 
-Typing the command
+%Typing the command
 
-\begin{Verbatim}[frame=single]
-> spider_params.plot_planet(t)
-\end{Verbatim}
+%\begin{Verbatim}[frame=single]
+%> spider_params.plot_planet(t)
+%\end{Verbatim}
 
-Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date (t).
-If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.
+%\begin{Verbatim}[frame=single]
+%> spider_params.plot_system(t)
+%\end{Verbatim}
 
-typing the command
-
-\begin{Verbatim}[frame=single]
-> spider_params.plot_system(t)
-\end{Verbatim}
-
-will generate a plot like figure \ref{fig:plot_system}, which is a scale diagram of the system.
-The desired phase or julian date can be given as an argument.
-These plots can be very useful for visualising the physical impacts of the chosen parameters.
+As well as lightcurve generation the code includes plotting functions to visualise the brightness or temperature distributions.
+An example plot is given in \ref{fig:plot_system}, which is a scale diagram of the system at a specified time or phase.
+Plots like this are useful for visualising the effects of varying the parameters.
 
@@
 \end{figure*}
-
-\textsc{spiderman} has been designed to ensure that it is easy to visualise the appearance of the model at all stages.
-
-\subsection{Performance}\label{sec:performance}
 
@@
 As a test of the performance of the code the model was applied to a phase curve and secondary eclipse of WASP-43b taken with HST WFC3.
-These data had previously been published in \citet{Stevenson2014}.
+These data have previously been published in \citet{Stevenson2014}.
 However, in this paper the phase curve and the secondary eclipse are treated as separate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
@@
 
-Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which serves to alleviate the degeneracy.
+Fortunately, the phasing of the observations is such that the three visits cover different portions of the phase curve, which helps to alleviate the degeneracy.
 
@@
 The results of both runs are presented In table \ref{tab:results}.
-There is very little difference between the fitted parameters with and without limb darkening.
-The value of $T_n$ is lower by more than $3\sigma$ in the fit with planetary limb darkening, but the other parameters in the physical model, $\Delta T$ and $\xi$ are consistent to within $2\sigma$ between the two runs.
-it is particularly worth noting how apparently unaffected $\xi$ is by the presence of limb darkening, the difference being much less than $1\sigma$.
-This makes sense, as $\xi$ effectively parametrises the asymmetry in the flux distribution, while the limb darkening is symmetrical.
-This is fortunate, as $\xi$ is the most physically interesting of the model parameter, and is directly tied to the details of heat transport in the atmosphere.
-The insensitivity of this parameter to limb darkening is important, as it shows that it can be recovered reliably even in ignorance of the vertical temperature structure of the planet's atmosphere.
+With the exception of $T_n$, which is lower by more than $3\sigma$ in the fit with planetary limb darkening, the physical parameters are consistent.
+In particular, $\xi$ seems only weakly affected by the presence of limb darkening, the difference being much less than $1\sigma$.
+This is not unexpected, as $\xi$ effectively parametrises the asymmetry in the flux distribution, while the limb darkening is symmetrical.
+$\xi$ is directly tied to the details of heat transport in the atmosphere, so the insensitivity of this parameter to limb darkening is useful, as it shows that it can be recovered even with systematic uncertainties in the flux distribution, so long as they are symmetric.
 
@@
 
-It is also interesting to check the correlation of this $\xi$ parameter with the other model parameters, this can be seen in the corner plot in figure \ref{fig:triangle corner sub}.
-$T_s$ and $\Delta T$ are clearly correlated parameters, which is logical, as between them they determine the average temperature of the dayside, which controls the amplitude of the phase curve.
-Crucially, $\xi$ is not strongly degenerate with the other parameters.
-This indicates that the $\xi$ parameter is robust to any errors in the absolute flux level of the system, due to, for example, not modelling the instrument response curve.
+The correlation between the physical model with the other model parameters can be seen in figure \ref{fig:triangle corner sub}.
+$T_s$ and $\Delta T$ are clearly correlated parameters, since between them they determine the average temperature of the dayside and hence the amplitude of the phase curve.
+$\xi$ is not strongly degenerate with the other parameters.
+This indicates that the $\xi$ parameter is robust to any errors in the absolute flux level of the system.
 
@@
 
-An intriguing difference between our model fit and the previous fit by \citet{Stevenson2014} is that we are able to infer a nightside temperature, where they were only able to place upper limits.
-To demonstrate that the flux from the nightside is a real feature in the model fit, and not an abstract parameterisation of some other feature, we investigate the flux level just outside of the primary transit.
-If the nightside has indeed been significantly detected, the flux here should be significantly different to the star-only flux visible during the secondary eclipse (which is 1.0 by definition).
+The model fit implies that the night-side of the planet is significantly hotter than expected at 1290 K \citet{Stevenson2014}.
+If the nightside has been significantly detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
 Drawing 10,000 lightcurves from the parameters in the non-limb darkened MCMC posterior, we plot the median, 1 sigma and 3 sigma contours for the lightcurve in figure \ref{fig:model}.
-The flux both just before, and just after the primary transit is significantly greater than 1.0 at the 3 sigma level, indicating that there is indeed flux detected from the night side of the planet.
+The flux is found to be significantly greater than 1.0 at the 3 sigma level.
 
@@
 
-As a test of the physical nature of this nightside flux, we repeat the fit with an additional model parameter which allows \emph{planetary} limb darkening or brightening.
+((Laura - comment on how bright nightside would be inconsistent with eclipse spectra?))
 
-Repeating this test with the limb darkened fit does not find significant night side flux, which casts doubt on the significance of this detection.
+Repeating this test with the limb darkened fit finds a significantly fainter night side flux, suggesting that the nightside flux is an artifact of using a simple physical model.
+This may be due to a correlation between model parameters making the fit inflexible and the simultaneous fit with the systematics model.
+Alternatively, the model may be unable to parametrise a feature of the nightside that is blocking the emitted flux, such as clouds.
 
-inhibit limb brightening or limb darkening \citep{Stevenson2014}.
-However, despite this unexpected result, as previously discussed, there is no significant difference to the physical model fit of \citep{Zhang2016}, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
+However, as previously pointed out, the $\xi$ parameter does not seem to be effected, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
 
@@
 \end{center}
+
+\subsubsection{Spectrally resolved}
 
@@
 We demonstrate the use of \textsc{spiderman} by applying the code to the case of WASP-43b.
-We use a physically motivated analytical model presented by \citet{zhang2016} which captures the major features of exoplanet phase curves.
+We use a physically motivated analytical model presented by \citet{Zhang2016} which captures the major features of exoplanet phase curves.
 We find that the model provides a good fit to the data, but overpredicts the nightside flux compared to non-informative models.
@@
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
-%\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
-%\caption{The underlying temperature distributions generated by the zhang model.}
-%\label{fig:best_fit_temp}
-%\end{center}
-%\end{figure*}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
+\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
+\caption{The underlying temperature distributions generated by the zhang model.}
+\label{fig:best_fit_temp}
+\end{center}
+\end{figure*}
 

### 2017-07-20 ms.tex
Update on Overleaf.

@@
 $^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
-$^{2}$Department of Astronomy, Harvard University, Cambridge, MA 02138, USA}
+$^{2}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
 
@@
 There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
-Hot Jupiters like HD\,189733b with, relatively temperatures have highly significant hotspot offsets and efficient day-night redistribution (cite examples other than HD 189).
+Hot Jupiters like HD\,189733b with, relatively low temperatures have highly significant hotspot offsets and efficient day-night redistribution \citep{Knutson2007b}.
 $\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
@@
 
-This behaviour has been anticipated in models (cite thad komacek?)
+This behavior can be explained with the results of General Circulation Models \citep{Komacek2015,Komacek2016}
 
@@
 
-A completely non-physics dependent model is a sum of spherical harmonics. This has been used before by ((cite)) an example generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}
+A useful and non-physics dependent model is a sum of spherical harmonics.
+This method was used for the case of the phase curve of HD\,189733b by \citet{Majeau2012}.
+An example map generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}.
+The main observational features of a phase curve, including the offset hotspot can typically be recovered with a only the first spherical harmonic, with the centre offset from the substellar point.
+\citep{Cowan2016} explore the effects of odd harmonics in phase curve data, and find that these correspond to weather features in the planet atmosphere.
 

### 2017-07-20 ms.tex
Update on Overleaf.

@@
 An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
-The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection (citation).
+The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection \citep{Showman2011}.
 
 An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be delayed from the time of secondary transit by a measurable amount.
-This effect can also be mimicked by a high eccentricity \citep{J.deWit2012a} (is this the right citation?).
+This effect can also be mimicked by a high eccentricity.
+\citet{J.deWit2012a} show that this is not the case for HD\,189733b using eclipse mapping.
 
@@
 
-\textsc{batman} \citep{Kreidberg2015a} is a fast and accurate analytical model of exoplanet primary transits, the code is open source and publicly available.
-\textsc{batman} serves as the inspiration for this project, as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
+\textsc{batman} \citep{Kreidberg2015a} is a fast analytical model of exoplanet primary transits, the code is open source.
+\textsc{batman}.
+as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
 

### 2017-07-20 ms.tex
Update on Overleaf.

@@
 Approximately 1000 models can be generated per second with typical parameters, making Markov Chain Monte Carlo analyses practicable.
+The modular nature of the code allows easy comparison of the effect of multiple different brightness distributions of the dataset.
 
-Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b.
-The model provides a good fit to the data, however, the best fitting model overpredicts the temperature of the night-side.
+As a test case we apply the code to archival data on the phase curve of WASP-43b using a physically motivated analytical model for the brightness model.
+The model provides a good fit to the data, however it overpredicts the temperature of the night-side.
 We speculate that this could be due to the presence of clouds on the night side of the planet.
+We also test for variation of the map parameters as a function of wavelength and find no statistically significant correlations.
 
-We test statistically for variation of the map parameters as a function of wavelength and find no statistically strong correlations.
-
-The development version of the code is available at \url{https://github.com/tomlouden/spiderman}.
+\textsc{spiderman} is available for download at \url{https://github.com/tomlouden/spiderman}.
 
@@
 Secondary eclipses and phase curves can give direct insight into the thermal transport processes, and when wavelength resolved also give information on the vertical structure of an exoplanet atmosphere.
-
-Hot Jupiters are expected to be tidally locked to their parent stars, resulting in a permanent day and night side with enormous differences in incident flux.
-The details of the heat transport in the atmosphere will effect how efficiently energy can be transported between the two hemispheres of the planet.
+The details of heat transport in the atmosphere will effect how efficiently energy can be transported between the two hemispheres of the planet.
 
@@
 
-An offset hotspot can be detected though the thermal phase-curve of the planet, as the point of maximum flux will be delayed from the time of secondary transit by a measurable amount.
-This effect can also be mimicked by a high eccentricity.
-\citet{J.deWit2012a} show that this is not the case for HD\,189733b using eclipse mapping.
-
-Hot Jupiters, with temperatures of order 1000 K are hot enough that they have appreciable infrared flux emission, affording contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
+The high equilibrium temperature of Hot Jupiters affords them contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
 \citet{Deming2005} detected the infrared flux of HD\,209458b by observing the secondary transit of the planet with the MIPS instrument on \emph{Spitzer}.
@@
 Intriguingly, the phase of this sinusoidal curve was significantly offset from the time of secondary eclipse, validating earlier predictions from GCM's.
+This effect can also be mimicked by a high eccentricity, but \citet{J.deWit2012a} show that this is not the case for HD\,189733b.
 
@@
 \citep{Harrington2006,Cowan2007,zellem2014}.
-
 This behavior can be explained with the results of General Circulation Models \citep{Komacek2015,Komacek2016}
@@
 The high velocity winds transporting this energy have been predicted to be on the order of kilometers per second, which would leave a measurable imprint on the spectral absorption lines in the planets atmosphere through Doppler shifting \citep[e.g.][]{Showman2013}, and indeed, this effect has been observed in the transit of HD\,209458b \citep{Snellen2010} and HD\,189733b \citep{Louden2015}.
-
-/%WASP-43b is similarly an extremely hot Jupiter, so would be expected to have high temperature contrast between day and night sides.
-The primary and secondary eclipses of this planet, as well as the phase curve, have been measured with HST WFC3 and reported in \citep{Stevenson2014}, and these data will be re-analysed here.
-
-Excitingly, it is possible to invert phase curves to give information on the longitudinal brightness distribution of the exoplanet, providing a way to map the surfaces of other worlds.
 
@@
 
-POTENTIAL OF JWST
+When phase curves are spectrally resolved, they can provide an extremely powerful tool for accessing the vertical structure of an exoplanet atmosphere as a function of longitude.
+\citet{Stevenson2014} use WFC3 on \textsc{HST} to measure the emission spectrum and recover the Temperature-Pressure profile of WASP-43b as a function of phase.
 
-\textsc{batman} \citep{Kreidberg2015a} is a fast analytical model of exoplanet primary transits, the code is open source.
-\textsc{batman}.
-as there does not currently exist an open source code for calculating both secondary eclipses and phase curves in a self consistent way, \textsc{spiderman} is designed to fulfil this role, and it is is hoped that it will be of use to the community.
+%JWST expectations?
 
-In this paper we first describe the model, and provide a brief overview of the use of the code, and then an example of use on the hot Jupiter WASP-43b.
+An open source code for calculating both exoplanet eclipses and phase curves in a self consistent way for arbitrary brightness distributions does not currently exist.
+\textsc{batman} \citep{Kreidberg2015a} is an open source code to model exoplanet primary transits with a fast C-based analytical integrator, making it suitable for use with MCMC's, and has found broad use in the exoplanet community.
+\textsc{spiderman} is designed to fulfill the same role for secondary eclipses and phase curves, and it is is hoped that it will be of use to the community.
+
+In this paper we first describe the model, and provide a brief overview of the code, and then an example of use on the hot Jupiter WASP-43b.
 
@@
 
-These models could also be used to represent the reflection of light due to clouds in optical phase curves. ((citations to K2 stuff, armstrong))
+These models could also be used to represent the reflection of light due to clouds in optical phase curves, which have been shown to be present, and even time varying in K2 data \citep{Armstrong2016}.
 
@@
 \citet{Zhang2016}.
-This model was developed as part of a simple analytical framework to describe the broad trends within complex GCM's, and does a remarkably good job of replicating the temperature distributions of GCM's with only three free parameters.
-These parameters are physical in nature, the Temperature of the nightside of the planet, $T_n$, the difference in Temperature between the day and night side, $\Delta T$, and the ratio between the advective and radiative timescales in the atmosphere, $\xi$.
+This model was developed as part of a simple analytical framework to describe the broad trends within complex GCM's, and does a good job of replicating the temperature distributions of GCM's with only three free parameters.
+These parameters are physically motivated; the Temperature of the nightside of the planet, $T_n$, the difference in Temperature between the day and night side, $\Delta T$, and the ratio between the advective and radiative timescales in the atmosphere, $\xi$.
 
-This is the first time a physical model of atmosphere circulation has been used to directly fit to data.
-
-The $\xi$ parameter is perhaps the most interesting, as it effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere.
+The $\xi$ parameter effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere.
 The effects of this can be seen in \ref{fig:ex_lcs}, where both the position of the maxima of the phase curve, and the shape of the ingress and egress of the secondary eclipse are clearly effected by this asymmetry.
@@
 These data have previously been published in \citet{Stevenson2014}.
-However, in this paper the phase curve and the secondary eclipse are treated as separate phenomena, when of course, they are both manifestations of the same underlying brightness distribution.
-Indeed, the bright dayside of the planet is the main driver of the phase curve, and is also the part occulted by the stellar disc.
-It is therefore more parsimonious, if at all possible, to use a model that accounts for both of these observations simultaneously.
-This also reduces the total number of parameters needed, which implies a better information content.
+However, in their paper the phase curve is fit with a sinusoid function.
+Here we instead apply the physically motivated model of \citet{Zhang2016} to test its applicability to observed data.
+This also reduces the total number of parameters needed for the fit.
 
-One could argue that planetary limb darkening, among other effects, will act to decouple the secondary eclipse from the phase curve, and there are not good constraints on what to expect from the limb darkening as it requires a full atmosphere model treatment.
-\textsc{spiderman} does have the option to include planetary limb darkening, which would allow one to marginalise over the uncertainty in these parameters.
-
-In principle, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet, however this would require a full radiative transfer treatment of the planet.
-
-As this effect is poorly understood, we run the fit both with and without planetary limb darkening.
-
-WASP-43b appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to a zero limb darkening.
-However, as discussed in \ref{sec:results}, we will show there is a preference in the fit for a \emph{limb brightened profile} which may indicate the presence of a weak thermal inversion layer, or may simply be due to oversimplifications in the model fit.
+Planetary Limb darkening is a potential sources of uncertainty on the final brightness distribution that would require more detailed atmosphere models to predict.
+\textsc{spiderman} has the option to include planetary limb darkening in addition to the chosen brightness model with a quadratic law.
+In principle, measurements of planetary limb darkening can constrain the vertical temperature profile of the planet, however this would require a full radiative transfer treatment calculation of the atmosphere.
+For the case of WASP-43b, limb darkening is not expected to be important, since the planet appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to zero limb darkening.
+We treat the additional freedom from the limb darkening as a test of the sensitivity to uncertainties of the radial brightness profile of the planet.
 
@@
 For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well \citet{Wakeford2016}.
-Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however there might be concerns that if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
+Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
 
@@
 
-An important early result from JWST will be a characterisation of the systematics, particularly for MIRI, as this will have significant consquencies for the practicality of phase curve and eclipse mapping observations with JWST.
+An important early result from JWST will be a characterization of the systematics, particularly for MIRI, as this will have significant consequences for the practicality of phase curve and eclipse mapping observations with JWST.
 
@@
 
-The initial parameter positions are found with a least squares minimisation approach, and the 1000 walkers were initialised around these best fitting values.
+The initial parameter positions are found with a least squares minimization approach, and the 1000 walkers were initialized around these best fitting values.
 
@@
 
-To test for the potential impact of \emph{planetary} limb darkening, we ran a second MCMC with this effect modelled by a simple quadratic limb darking law.
+To test for the potential impact of \emph{planetary} limb darkening, we ran a separate MCMC with this effect modeled by a simple quadratic limb darking law with parameters $p_{u1}$ and $p_{u2}$.
 We place the constraint that the limb darkening must be monotonic across the disc of the planet, i.e., there can be no change in the sign of the gradient.
@@
 
-The model fit implies that the night-side of the planet is significantly hotter than expected at 1290 K \citet{Stevenson2014}.
-If the nightside has been significantly detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
+The model fit implies that the night-side of the planet is significantly hotter than expected at 1290 $\pm 39$ K, whereas it is not significantly detected in \citet{Stevenson2014}.
+If the nightside has been detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
 Drawing 10,000 lightcurves from the parameters in the non-limb darkened MCMC posterior, we plot the median, 1 sigma and 3 sigma contours for the lightcurve in figure \ref{fig:model}.
-The flux is found to be significantly greater than 1.0 at the 3 sigma level.
+The flux is found to be greater than 1.0 at the 3 sigma level.
 
@@
 
-((Laura - comment on how bright nightside would be inconsistent with eclipse spectra?))
+%((Laura - comment on how bright nightside would be inconsistent with eclipse spectra?))
 
-Repeating this test with the limb darkened fit finds a significantly fainter night side flux, suggesting that the nightside flux is an artifact of using a simple physical model.
+The fit with limb darkening finds a significantly fainter night side flux, suggesting that the nightside flux is an artifact of using a simple physical model.
 This may be due to a correlation between model parameters making the fit inflexible and the simultaneous fit with the systematics model.
@@
 
-However, as previously pointed out, the $\xi$ parameter does not seem to be effected, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
+However, we emphasize that the $\xi$ parameter does not seem to be effected, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
 
@@
 \subsubsection{Spectrally resolved}
+
+Spectrally resolving the phase offset in principle allows information on the heat transport as a function of depth.
+To test for this effect we break the data down into 15 spectral bins and repeat the MCMC analysis described for the white light data, without allowing the additional radial freedom from limb darkening.
+We fix the system parameters to those found in the white light fight.
+We report the measurement of $\xi$ parameter as a function of wavelength in table
 
@@
 
-The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonathan Fortney and Pascale Garaud.
+T.L.
+is supported by STFC consolidated grant (ST/L000733/1).
+Much of this work was carried out at the kavli summer program in physics 2016.
+T.L extends his gratitude to the program organisers, in particular Jonathan Fortney and Pascale Garaud.
 

### 2017-08-01 ms.tex
Update on Overleaf.

@@
 % Keep the title short and informative.
-\title[SPIDERMAN]{SPIDERMAN: an open source code to model phase curves and secondary eclipses.}
+\title[SPIDERMAN]{SPIDERMAN: an open-source code to model phase curves and secondary eclipses}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
+\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2,3}$\\
 $^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
-$^{2}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
+$^{2}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA
+$^{3}$Harvard Society of Fellows, Cambridge, MA 02138, USA}
 
@@
 
-Presenting \textsc{spiderman}, a fast code for calculating exoplanet phase curves and secondary eclipses with arbitrary surface brightness distributions.
+We present \textsc{spiderman}, a fast code for calculating exoplanet phase curves and secondary eclipses with arbitrary surface brightness distributions.
 
@@
 
-General Circulation Models (GCM's), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}.
-An important early prediction of these GCM's was that hot, tidally locked Jupiter's would display significantly offset hotpots.
+General Circulation Models (GCMs), are currently the state of the art for predicting the wind patters and temperature distributions of the surface of exoplanets \citep[e.g.][]{Showman2008}.
+An important early prediction of these GCMs was that hot, tidally locked Jupiters would display significantly offset hotpots.
 The hotspot offset is the result of fast superotating equatorial winds in the atmosphere that arise from a coupling of planetary scale circulation and day night advection \citep{Showman2011}.
 
-The high equilibrium temperature of Hot Jupiters affords them contrasts with their parents stars of order 0.1\%, making direct detection with current generation instruments feasible.
+The high equilibrium temperature of Hot Jupiters affords them contrasts with their parent stars of order 0.1\%, making direct detection with current generation instruments feasible.
 \citet{Deming2005} detected the infrared flux of HD\,209458b by observing the secondary transit of the planet with the MIPS instrument on \emph{Spitzer}.
-Using the IRAC instrument on \emph{Spitzer}, \citet{Knutson2007b} went on to measure the secondary eclipse of HD\,189733b with high precision, and also show that the system displayed a sinusoidal \emph{phase curve}, caused by the bright regions of the planet rotating into and out of view.
-Intriguingly, the phase of this sinusoidal curve was significantly offset from the time of secondary eclipse, validating earlier predictions from GCM's.
+Using the \emph{Spitzer}/IRAC, \citet{Knutson2007b} went on to measure the secondary eclipse of HD\,189733b with high precision, and also show that the system displayed a sinusoidal \emph{phase curve}, caused by the bright regions of the planet rotating into and out of view.
+Intriguingly, the phase of this sinusoidal curve was significantly offset from the time of secondary eclipse, validating earlier predictions from GCMs.
 This effect can also be mimicked by a high eccentricity, but \citet{J.deWit2012a} show that this is not the case for HD\,189733b.
@@
 
-\cite{Majeau2012} showed that as well as mapping longitudinally with phase curves, it is possible to get a two dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non zero impact parameter.
+\cite{Majeau2012} showed that as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter.
 This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress.
@@
 When phase curves are spectrally resolved, they can provide an extremely powerful tool for accessing the vertical structure of an exoplanet atmosphere as a function of longitude.
-\citet{Stevenson2014} use WFC3 on \textsc{HST} to measure the emission spectrum and recover the Temperature-Pressure profile of WASP-43b as a function of phase.
+\citet{Stevenson2014} use the Wide Field Camera 3 instrument on the Hubble Space Telescope \textsc{HST}/WFC3 to measure the emission spectrum and recover the temperature-pressure profile of WASP-43b as a function of phase.
 
@@
 
-An open source code for calculating both exoplanet eclipses and phase curves in a self consistent way for arbitrary brightness distributions does not currently exist.
-\textsc{batman} \citep{Kreidberg2015a} is an open source code to model exoplanet primary transits with a fast C-based analytical integrator, making it suitable for use with MCMC's, and has found broad use in the exoplanet community.
-\textsc{spiderman} is designed to fulfill the same role for secondary eclipses and phase curves, and it is is hoped that it will be of use to the community.
+An open-source code for calculating both exoplanet eclipses and phase curves in a self-consistent way for arbitrary brightness distributions does not currently exist.
+\textsc{batman} \citep{Kreidberg2015a} is an open source code to model exoplanet primary transits with a fast C-based analytical integrator, making it suitable for use with MCMCs, and has found broad use in the exoplanet community.
+\textsc{spiderman} is designed to fulfill the same role for secondary eclipses and phase curves, and it is our hope that it will be of use to the community.
 
@@
 
-In order to accurately calculate both the phase curve and secondary eclipse the code must integrate over the portion of the planet that is facing the observer and is not occulted by the star at each time-step.
+In order to accurately calculate both the phase curve and secondary eclipse the code must integrate over the portion of the planet that is facing the observer and is not occulted by the star at each time step.
 In order to be general use and ``model agnostic'' the integrator cannot assume any specific properties or symmetries in the brightness distribution.
-This can be done numerically, by sampling a grid of points on the planets surface and summing those that are visible, but to achieve high precisions a large number of points would need to be sampled, which would be slow and computationally inefficient.
+This can be done numerically, by sampling a square grid of points on the planet's surface and summing those that are visible, but to achieve high precisions a large number of points would need to be sampled, which would be slow and computationally inefficient.
 
-Instead, \textsc{spiderman} uses an analytical integration scheme where the planet is divided into a relatively small number of regions, and the area of each region that is not occulted by the star is calculated exactly through geometry.
+Instead, \textsc{spiderman} uses a novel integration scheme where the planet is divided into a relatively small number of regions, and the area of each region that is not occulted by the star is calculated exactly through geometry.
 The average surface brightness of each region is determined by the chosen model and multiplied by the visible area to get the total flux.
@@
 \textsc{spiderman} uses a radial co-ordinate system centered on the visible hemisphere of the planet.
-The planet is defined to have a radius of 1 and the visible disc of the planet is divided into a series of annuli, and then these in turn are separated in theta, see the schematic in figure \ref{fig:schematic}.
-The number of segments in each annuli are chosen so that the area of every sector is the same.
-This results in 1 circular segment in the center, then 3 regions in the second annuli and 5 in the third - with the number of segment in the nth annuli being 2n - 1.
-Using this scheme, dividing the planet n times radially results in a total of n$^2$ integration elements.
+The planet is defined to have a radius of unity and the visible disc of the planet is divided into a series of annuli, and then these in turn are separated in polar angle $\theta$, as shown in the schematic in Figure \ref{fig:schematic}.
+The number of segments in each annulus are chosen so that the area of every sector is the same.
+This results in one circular segment in the center, then three regions in the second annuli and five in the third - with the number of segment in the $n$th annulus being $2n - 1$.
+Using this scheme, dividing the planet $n$ times radially results in a total of $n^2$ integration elements.
 
@@
 Therefore, the first step for calculating the occulted area for each segment of the planet is to calculate these collision points.
-Within \textsc{spiderman} the region boandaries are stored as the radius of the inner and outer arcs, and the $\theta$ angle of the two radial lines.
+Within \textsc{spiderman} the region boundaries are stored as the radius of the inner and outer arcs, and the $\theta$ angle of the two radial lines.
 
 Finding the collision points between an arc or a line and a circle (the star), if any exist, are trivial and fast to calculate.
-The code then classifies the geometric ``case" of the collision based on the number of collision points on the 4 boundary sides.
+The code then classifies the geometric ``case" of the collision based on the number of collision points on the four boundary sides.
 
@@
 Numerical errors can be introduced by this approach if the brightness distribution changes significantly faster than the area elements, but the size of the elements can be adjusted as necessary by the user, at the cost of computation time.
-In practice, we found that dividing the planet into 5 radially (giving 25 total elements) gave sufficient precision for the smoothly varying brightness profile in our WASP-43b test case, and increasing the mesh density beyond this point did not change the results.
+In practice, we found that dividing the planet into five radial segments (25 total elements) gave sufficient precision for the smoothly varying brightness profile in our WASP-43b test case, and increasing the mesh density beyond this point did not change the results.
+Other grid schemes could also be defined by the user.
+For example, if the information content is higher in some parts of the planet than others, then the grid could be made finer in these regions.
 
-Other grid schemes could be defined, for example, if it is decided that the information content is higher in some parts of the planet than others then the grid could be made finer in these regions.
-
-We performed a simple validation check to demonstrate that the integrator is working correctlyl.
-assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have no impact on the final light-curve.
+We performed a simple validation check to demonstrate that the integrator is working correctly.
+Assuming a uniform brightness distribution, the number of sections that the planet is broken into for the integration should have no impact on the final light curve.
 
 To test that the integrator is performing correctly we compare the case of a single segment model, i.e., a circle, for which there is a single analytical solution to the area blocked by another circle, to one with 400 segments.
-In both cases the planet is assumed to have a total luminosity that is 1\% that of the star's.
+In both cases the planet is assumed to have a total luminosity that is 1\% that of the star.
 
-A lightcurve is calculated for each of these cases, and then the difference is taken.
-The results of this test can be seen in figure \ref{fig:precision}, where it is clear that there is no difference between the two lightcurves greater than floating point precision (2.22e-16).
+A light curve is calculated for each of these cases, and then the difference is taken.
+The results of this test can be seen in Figure \ref{fig:precision}, where it is clear that there is no difference between the two light curves greater than floating point precision (2.22e-16).
 We therefore consider the geometric integrator of \textsc{spiderman} to be validated.
@@
 
-\subsection{The brightness models}\label{sec:temp model}
+\subsection{Brightness models}\label{sec:temp model}
 
 \textsc{spiderman} has been written in a modular way, so that users will be able to choose from a variety of models to fit to their data, or provide their own.
-
-The currently availible models range from fully non-informative to basic physical models, and also utilities to allow the results of forward models to be quickly converted into phase curves and eclipses.
-
-\textsc{spiderman} projects this temperature map onto the visible sphere of the planet, meaning it is used directly to calculate the secondary eclipse and phase curve.
+The currently available models range from fully non-informative to basic physical models.
+We also provide utilities to allow the results of forward models to be quickly converted into phase curves and eclipses.
+\textsc{spiderman} projects the model temperature map onto the visible sphere of the planet, and then directly calculates the secondary eclipse and phase curve.
 
@@
 
-A useful and non-physics dependent model is a sum of spherical harmonics.
+A useful and physics-independent model is a sum of spherical harmonics.
 This method was used for the case of the phase curve of HD\,189733b by \citet{Majeau2012}.
-An example map generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}.
-The main observational features of a phase curve, including the offset hotspot can typically be recovered with a only the first spherical harmonic, with the centre offset from the substellar point.
+An example map generated by \textsc{spiderman} is displayed in Figure \ref{fig:harmonics}.
+The main observational features of a phase curve, including the offset hotspot, can typically be recovered with a only the first spherical harmonic, with the centre offset from the substellar point.
 \citep{Cowan2016} explore the effects of odd harmonics in phase curve data, and find that these correspond to weather features in the planet atmosphere.
@@
 
-The simplest physically model that one construct involve defining a bulk planetary temperature or flux, and then a "Hotspot" where the contrast and offset from the substellar point in longitude and latitude are model parameters.
-Models where the day and the night side have different fluxes are a subset of these models.
-
-These models could also be used to represent the reflection of light due to clouds in optical phase curves, which have been shown to be present, and even time varying in K2 data \citep{Armstrong2016}.
+The simplest physical model that one can construct involves defining a bulk planetary temperature or flux, and then a "hotspot" where the size, contrast, and offset from the substellar point in longitude and latitude are model parameters.
+This model can be used to represent a "two-temperature" planet with different fluxes on the dayside versus the nightside.
+The hotspot model could also be used to represent the reflection of light due to clouds in optical phase curves, which have been shown to be present and even time varying \citep{Armstrong2016}.
 
@@
 
-\citet{Zhang2016}.
-This model was developed as part of a simple analytical framework to describe the broad trends within complex GCM's, and does a good job of replicating the temperature distributions of GCM's with only three free parameters.
-These parameters are physically motivated; the Temperature of the nightside of the planet, $T_n$, the difference in Temperature between the day and night side, $\Delta T$, and the ratio between the advective and radiative timescales in the atmosphere, $\xi$.
+We implement the kinematic model from \citet{Zhang2016}, which is a simple analytic function that does a good job of replicating the temperature distributions of GCMs with only three free parameters.
+These parameters are physically motivated; the temperature of the nightside of the planet, $T_n$, the difference in temperature between the day and night side, $\Delta T$, and the ratio between the advective and radiative timescales in the atmosphere, $\xi$.
 
@@
 \textsc{spiderman} also has the capability to quickly calculate a phase curve and secondary eclipse from a pre-calculated forward model.
-The code can read in a grid of either temperatures or brightnesses, in longitude and latitude, and will use a two dimensional bicubic interpolation within this grid to assign brightnesses to the grid points at each time-step.
+The code can read in a grid of either temperatures or brightnesses, in longitude and latitude, and will use a two dimensional bicubic interpolation within this grid to assign brightnesses to the grid points at each time step.
 Continuity is assumed east-west and across the poles to minimise edge effects.
@@
 
-\subsection{Lightcurve calculation}\label{sec:lightcurve}
+\subsection{Light curve calculation}\label{sec:lightcurve}
 
-The primary purpose of \textsc{spiderman} is to produce lightcurves to compare with the data.
-Now that the functioning of the geometric integrator has been described, lightcurve generation is quite simple.
+The primary purpose of \textsc{spiderman} is to produce light curves to compare with the data.
+Now that the functioning of the geometric integrator has been described, light curve generation is quite simple.
 
-Given a series of time points, the ephemeris of the system, the system scale and the planet star radius ratio, the position of the planet relative to the star can be calculated for each timestep.
+Given a series of points in time, the ephemeris of the system, the system scale and the planet/star radius ratio, the position of the planet relative to the star can be calculated for each timestep.
 Light time of travel effects are accounted for, with the semi-major axis in physical units as a parameter.
 
-Since it is assumed that the planet is tidally locked, at each timestep the geometric grid representing the planet is populated with the appropriate fluxes from the chosen flux distribution model.
+Since we assume that the planet is tidally locked, at each time step the geometric grid representing the planet is populated with the appropriate fluxes from the chosen flux distribution model.
 
@@
 This is quickly achieved by checking for contact between the edges of the region and the edge of the star.
-If there are no contact points, and the distance from the center point to the center point of the star is greater than the stellar radius, then the segment is fully visible, and the full flux is counted, if the distance is less then the stellar radius then it is fully occulted and no flux is added.
+If there are no contact points, and the distance from the center point to the center point of the star is greater than the stellar radius, then the segment is fully visible, and the full flux is counted.
+If the distance is less then the stellar radius, then it is fully occulted and no flux is added.
 For cases of partial coverage, the previously described geometric integrator is used to calculate the flux that should be added.
 
-To this, the pre-calculated stellar total flux is added to give the total system flux. This is then divided by the stellar flux to give a relative lightcurve that can easily be compared to data.
+To this, the pre-calculated stellar total flux is added to give the total system flux. This is then divided by the stellar flux to give a relative light curve that can easily be compared to data.
 
 Note that \textsc{spiderman} does not calculate primary transits.
-To fit models to data that contain both primary and secondary eclipses, \textsc{spiderman} should be combined with another package such as BATMAN.
-The parameter naming convention and call sequence from \textsc{spiderman} has been chosen to be compatible with BATMAN for this reason.
+To fit models to data that contain both primary and secondary eclipses, \textsc{spiderman} should be combined with another package such as \textsc{batman}.
+The parameter naming convention and call sequence from \textsc{spiderman} has been chosen to be compatible with \textsc{batman} for this reason.
 
@@
 
-\textsc{spiderman} is an open source project and is being actively developed on github. The code is available on PyPi and github at \url{https://github.com/tomlouden/spiderman}.
+\textsc{spiderman} is an open-source project and is being actively developed on github. The code is available on PyPI and github at \url{https://github.com/tomlouden/spiderman}. 
+Installation instructions and documentation are available at \url{http://spiderman.readthedocs.io}
 
@@
 %\end{Verbatim}
-
-Installation instructions and documentation are available at \url{http://spiderman.readthedocs.io}
 
@@
 
-As well as lightcurve generation the code includes plotting functions to visualise the brightness or temperature distributions.
-An example plot is given in \ref{fig:plot_system}, which is a scale diagram of the system at a specified time or phase.
-Plots like this are useful for visualising the effects of varying the parameters.
-
 \begin{figure*}
@@
 
-In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core. This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.
-
+The code is written in Python with C extensions, and was optimized to run quickly.
+In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core.
+This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.
 Figure \ref{fig:exec_time} shows the result of a performance test carried out on a single core of an Intel Core I5-3470 Processor.
-The length of time to produce a model with 1000 timepoints as a function of the number of segments of the model.
+The length of time to produce a model with 1000 time points as a function of the number of segments of the model.
 The test shows that the execution time scales linearly with the number of segments in the model, which is expected, showing the overhead to run the model is very small.
 The precision required for typical usage can easily be reached using 16 or 25 segments, but larger numbers of segments can be used to produce better looking diagrams.
-The diagrams in this paper were generated with a 400 segment model.
+The diagrams in this paper were generated with a 400-segment model.
+
+In addition to light curve generation, \textsc{spiderman} also includes plotting functions to visualise the brightness or temperature distributions.
+An example plot is given in \ref{fig:plot_system}, which is a scale diagram of the system at a specified time or phase.
+Plots like this are useful for visualising the effects of varying the parameters.
 
@@
 
-As a test of the performance of the code the model was applied to a phase curve and secondary eclipse of WASP-43b taken with HST WFC3.
+We tested \textsc{spiderman}'s performance for a phase curve and secondary eclipse of the hot Jupiter WASP-43b observed with \emph{HST}/WFC3.
 These data have previously been published in \citet{Stevenson2014}.
@@
 
-Planetary Limb darkening is a potential sources of uncertainty on the final brightness distribution that would require more detailed atmosphere models to predict.
+Planetary limb darkening is a potential sources of uncertainty on the final brightness distribution that would require more detailed atmosphere models to predict.
 \textsc{spiderman} has the option to include planetary limb darkening in addition to the chosen brightness model with a quadratic law.
-In principle, measurements of planetary limb darkening can constrain the vertical temperature profile of the planet, however this would require a full radiative transfer treatment calculation of the atmosphere.
+In principle, measurements of planetary limb darkening can constrain the vertical temperature profile of the planet; however, this would require a full radiative transfer treatment calculation of the atmosphere.
 For the case of WASP-43b, limb darkening is not expected to be important, since the planet appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to zero limb darkening.
@@
 
-As with most exoplanet observations with Hubble, the data are effected by the idiosyncratic systematic errors of the instrument.
-Fortunately, the sources of these errors are relatively well understood, and are generally quite repeatable between observations.
-They are therefore quite straightforward to fit for and remove.
+As with most exoplanet observations with \emph{Hubble}, the data are effected by the instrument-based systematic errors.
+Fortunately, the sources of these errors are relatively well understood, and are generally repeatable between observations.
+They are therefore straightforward to fit for and remove.
 
 The systematics have effects on scales of \emph{visits}, \emph{orbits} and individual exposures, where a visit is a continuous set of orbits directed at a target.
-Due to the low earth orbit of Hubble, each complete orbit lasts 95 minutes, and for approximately half of this time the target will be unobservable due to being behind the Earth.
+Due to the low earth orbit of \emph{Hubble}, each complete orbit lasts 96 minutes, and for approximately half of this time the target will be unobservable because it is behind the Earth.
 For this reason, a complete exoplanet transit can not be observed with one ``visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.
-
-In this study, three visits, each with 12 orbits was used to cover the full phase of WASP-43.
-The phasing can be seen in figure \ref{fig:systematics}, and a phase folded lightcurve can be seen in figure \ref{fig:phase folded}
+In this study, three visits, each with 13 or 14 orbits was used to cover the full phase of WASP-43.
+The phasing can be seen in Figure \ref{fig:systematics}, and a phase-folded lightcurve can be seen in Figure \ref{fig:phase folded}
 
@@
 There are three components to the systematics model, the scan direction offset, ``hook effect'' and visit long slopes.
-
-The scan direction offset is depends on which way the the ccd was scanning during the readout, in one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the offset.
+The scan direction offset depends on which way the the detector was scanning during the readout.
+In one half of exposures the scan direction is in the same direction as the readout, and in the other half it is the opposite.
 This leads to a very repeatable offset in the fluxes between the two scan directions, which can be captured with a single parameter \emph{scale}
 
-Each orbit displays a characteristic exoplential ``hook'' signal, which can be modelled as
+Each orbit displays a characteristic exoponential ``ramp'' signal, which can be modelled as
 \begin{equation} \label{eq:hook}
-F_{cor} = F*(1-exp(-r1 t_{orb}-r2-r3 \delta_{fo}))
+F_{cor} = F*(1-\exp(-r1 t_\mathrm{orb}-r2-r3 \delta_\mathrm{fo}))
 \end{equation}
-Where $F$ is the flux before correction and $F_{cor}$ is the corrected flux $t_{orb}$ is the time from the start of each \emph{obit}, $r1$, $r2$, $r3$ are the fitted coefficients.
-This exponential ramp has a different shape during the first orbit of a visit, so the $\delta_{fo}$ function takes a value of 1 if the orbit is the first, and 0 at all other times.
-The exponential hook shape is believed to be related to charge trapping, and is a characteristic and repeatable feature across orbits, so these parameters are fit simultaneously over visits.
+Where $F$ is the flux before correction and $F_{cor}$ is the corrected flux $t_{orb}$ is the time from the start of each \emph{orbit}, $r1$, $r2$, $r3$ are the fitted coefficients.
+This exponential ramp has a different shape during the first orbit of a visit, so the $\delta_\mathrm{fo}$ function takes a value of 1 if the orbit is the first, and 0 at all other times.
+The exponential ramp shape is believed to be related to charge trapping, and is a characteristic and repeatable feature across orbits, so these parameters are fit simultaneously over visits.
 
 Each \emph{visit} displays a decreasing slope, which is modelled as a second order polynomial.
-The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \cite{Wakeford2016}.
-Here, they are also likely blended with the ``Breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
-The shape of these visit long effects is slightly different between the three visits used here, so the three paramters of the polynomial are fit seperately for the three visits.
+The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \citep{Wakeford2016}.
+Here, they are also likely blended with the ``breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
+The shape of these visit-long effects is slightly different between the three visits used here, so the three parameters of the polynomial are fit seperately for the three visits.
 
-The feature that is the greatest cause for concern is the visit long slope in the data, as this has a comparable timescale and amplitude to the planet's phase curve, so there is potential for degeneracies between the systematics and physical models.
-
+The feature that is the greatest cause for concern is the visit-long slope in the data, as this has a comparable timescale and amplitude to the planet's phase curve, so there is potential for degeneracies between the systematics and physical models.
 Fortunately, the phasing of the observations is such that the three visits cover different portions of the phase curve, which helps to alleviate the degeneracy.
 
-For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well \citet{Wakeford2016}.
-Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
-
+For \emph{HST} systematics, where the major sources of error are fairly well understood, a parameterised systematics model of this form works well \citet{Wakeford2016}.
+Alternatively, detailed instrumental models can recover the same features with fewer free parameters.
+However, if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.
 An alternative, powerful technique which does not make assumptions about the form of the systematics is Gaussian Processes \citep[e.g.][]{Gibson2012a}.
@@
 
-An important early result from JWST will be a characterization of the systematics, particularly for MIRI, as this will have significant consequences for the practicality of phase curve and eclipse mapping observations with JWST.
+An important early result from JWST will be a characterization of the systematics, particularly for the mid-infrared MIRI instrument, as this will have significant consequences for the practicality of phase curve and eclipse mapping observations with JWST.
 
@@
 The initial parameter positions are found with a least squares minimization approach, and the 1000 walkers were initialized around these best fitting values.
-
-For the orbital and system parameters we use published values and errorbars as priors.
-For the Period, inclination and $a/R_*$ we use the results of \citet{Hoyer2016}, and for $a$ the value from \citet{Hellier2011a}, The eccentricity was fixed at 0, which is supported by the findings of \citet{Hoyer2016}.
+For the orbital and system parameters we use published values and error bars as priors.
+For the period, inclination and $a/R_*$ we use the results of \citet{Hoyer2016}, and for $a$ the value from \citet{Hellier2011a}, The eccentricity was fixed at zero, which is supported by the findings of \citet{Hoyer2016}.
 The stellar log g and effective temperature priors are from \citet{Gillon2012}.
@@
 
-For both models, the MCMC was run for 10 million steps, with the first 200,000 steps discarded as burn in.
+For both models, the MCMC was run for 10 million steps, with the first 200,000 steps discarded as burn-in.
 
@@
 
-The best fitting model and the residuals are shown in figure \ref{fig:phase folded} as a function of planetary phase, after correction for instrument systematics.
-The data and model are also plotted as a function of time in figure \ref{fig:systematics}.
+The best fitting model and the residuals are shown in Figure \ref{fig:phase folded} as a function of planetary phase, after correction for instrument systematics.
+The data and model are also plotted as a function of time in Figure \ref{fig:systematics}.
 To demonstrate the systematics model the data are plotted with and without systematics correction.
@@
 
-The model fit implies that the night-side of the planet is significantly hotter than expected at 1290 $\pm 39$ K, whereas it is not significantly detected in \citet{Stevenson2014}.
+The model fit implies that the nightside of the planet is significantly hotter than expected at 1290 $\pm 39$ K, whereas it is not significantly detected in \citet{Stevenson2014}.
 If the nightside has been detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
@@
 
-\subsubsection{Spectrally resolved}
+\subsubsection{Spectrally-resolved phase curves}
 
@@
 To test for this effect we break the data down into 15 spectral bins and repeat the MCMC analysis described for the white light data, without allowing the additional radial freedom from limb darkening.
-We fix the system parameters to those found in the white light fight.
-We report the measurement of $\xi$ parameter as a function of wavelength in table
+We fix the system parameters to those found in the white light fit.
+We report the measurement of $\xi$ parameter as a function of wavelength in Table \ref{tab:specresults}.
 
@@
 
-The C based algorithm analytically calculates the area occulted of radial segments on the planet's surface, and is designed to run rapidly to enable statistical techniques such as MCMCs to run quickly.
+The C-based algorithm analytically calculates the area occulted of radial segments on the planet's surface, and is designed to run rapidly to enable statistical techniques such as MCMCs to run quickly.
 

### 2017-08-13 ms.tex

@@
 Using a geometrical algorithm, the code solves exactly the area of sections of the disc of the planet that are occulted by the star.
-The code is written in C and optimised to run quickly, with no loss in precision.
+The code is written in C with a user-friendly Python interface, and is optimised to run quickly, with no loss in precision.
 Approximately 1000 models can be generated per second with typical parameters, making Markov Chain Monte Carlo analyses practicable.
@@
 
-Secondary eclipses and phase curves can give direct insight into the thermal transport processes, and when wavelength resolved also give information on the vertical structure of an exoplanet atmosphere.
-The details of heat transport in the atmosphere will effect how efficiently energy can be transported between the two hemispheres of the planet.
+Secondary eclipses and phase curves can give direct insight into the climate of exoplanet atmospheres.
+The details of heat transport in the atmosphere will effect how efficiently energy can be transported between the two hemispheres of the planet, controlling the day-night contrast, and persistent wind patterns can move the brightest point of the planet from the sub-stellar point.
+As different wavelengths probe different depths of the atmosphere, spectroscopic phase curves and eclipses also contain information on the vertical temperature structure.
 
@@
 
-There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport.
-Hot Jupiters like HD\,189733b with, relatively low temperatures have highly significant hotspot offsets and efficient day-night redistribution \citep{Knutson2007b}.
+There appear to be two broad classes of exoplanet atmosphere heat circulation.
+Hot Jupiters like HD\,189733b, with relatively low temperatures have highly significant hotspot offsets and efficient day-night redistribution \citep{Knutson2007b}.
 $\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy.
@@
 
-\cite{Majeau2012} showed that as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter.
+As well as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter \citep{Rauscher2007}.
 This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress.
 The brightness distribution of the planet's permanent dayside will be imprinted on the precise shape of the ingress and egress curves.
+This has been demonstrated for HD\,189733 b by \citep{Majeau2012} ((and others))
 
@@
 
+In the past, authors studying phase curves have generally used non-physically motivated models to fit the data, such as sine curves ((cite)) or orange slices ((cite)).
+Whilst these approaches are still useful, \emph{spiderman} enables a \emph{direct} fit to the underlying distribution, and an easy way to compare different models.
+
 In this paper we first describe the model, and provide a brief overview of the code, and then an example of use on the hot Jupiter WASP-43b.
@@
 
-\subsection{Analytical integrator}\label{sec:integrator}
+\subsection{Integration scheme}\label{sec:integrator}
 
@@
 We also provide utilities to allow the results of forward models to be quickly converted into phase curves and eclipses.
-\textsc{spiderman} projects the model temperature map onto the visible sphere of the planet, and then directly calculates the secondary eclipse and phase curve.
+\textsc{spiderman} projects the model temperature or brightness map onto the visible sphere of the planet, and then directly calculates the secondary eclipse and phase curve.
+The option also exists to include an additional \emph{planetary} limb darkening component to the brightness distribution, which is parameterised as a quadratic law.
+The major currently available models are listed below.
 
@@
 This model can be used to represent a "two-temperature" planet with different fluxes on the dayside versus the nightside.
-The hotspot model could also be used to represent the reflection of light due to clouds in optical phase curves, which have been shown to be present and even time varying \citep{Armstrong2016}.
+The hotspot model could also be used to represent the reflection of light due to clouds in optical phase curves, which have been shown to be present in K2 lightcurves \citep{Demory2013} and are even found to be time varying in HAT-P-7 \citep{Armstrong2016}.
 
@@
 
+\textsc{spiderman} models the stellar spectrum using a grid of PHOENIX stellar atmospheres calculated by \citet{Husser2013}.
+It is also possible to use alternative models, or a simple blackbody spectrum, which will typically be sufficient for broadband observations.
+Using the user provided wavelength bandpass and instrument response, \textsc{spiderman} calculates the total observed flux for the stellar models as a function of effective temperature, it then interpolates on this grid using a spline.
+
 Since the shape and depth of an eclipse and phase curve are determined by the \emph{ratio} of the fluxes between the two bodies, there will clearly be an exact degeneracy between the planet and star brightness.
@@
 These additional parameters fix the flux scale of the system, allowing useful constraints to be placed on the absolute surface flux and brightness temperature of the planet.
-
-\textsc{spiderman} models the stellar spectrum using a grid of PHOENIX stellar atmospheres calculated by \citet{Husser2013}.
-Using the user provided wavelength bandpass and instrument response, \textsc{spiderman} calculates the total observed flux for the available models as a function of effective temperature, it then interpolates on this grid using a spline.
 
@@
 It was generated with the spiderman.plot\_system() command.
-The image of the star is purely aesthetic.}
+The image of the star is purely aesthetic and is not related to any model parameters (image credit SDO)}
 \label{fig:plot_system}
@@
 In principle, measurements of planetary limb darkening can constrain the vertical temperature profile of the planet; however, this would require a full radiative transfer treatment calculation of the atmosphere.
-For the case of WASP-43b, limb darkening is not expected to be important, since the planet appears to have a near isothermal profile \citep{Stevenson2014}, which should correspond to zero limb darkening.
-We treat the additional freedom from the limb darkening as a test of the sensitivity to uncertainties of the radial brightness profile of the planet.
+For the case of WASP-43b, where the limb darkening is unknown, we initially fix the limb darkening to zero, and then test the impact of varying the limb darkening, treating the additional freedom as a test of the sensitivity to uncertainties of the radial brightness profile of the planet.
 
@@
 The cause of these features is unknown, and they have not been linked to any physical parameters of the telescope \citep{Wakeford2016}.
-Here, they are also likely blended with the ``breathing" systematics of the instrument, which are caused by the changing thermal environment of the telescope during its orbit changing the focal length of the instrument.
 The shape of these visit-long effects is slightly different between the three visits used here, so the three parameters of the polynomial are fit seperately for the three visits.
@@
 
-For both models, the MCMC was run for 10 million steps, with the first 200,000 steps discarded as burn-in.
+For both models, the MCMC was run for 10 million steps, with the first 200,000 steps discarded as burn-in. Convergence was checked by visual inspection of the chains for each model parameter.
 
@@
 
+The model fit implies that the nightside of the planet is significantly hotter than expected at 1290 $\pm 39$ K, whereas it is not significantly detected in \citet{Stevenson2014}.
+If the nightside has been detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
+Drawing 10,000 lightcurves from the parameters in the non-limb darkened MCMC posterior, we plot the median, 1 sigma and 3 sigma contours for the lightcurve in figure \ref{fig:model}.
+The flux is found to be greater than 1.0 at the 3 sigma level.
+
+The visual representation of the flux maps for the non-limb darkened case can be seen in figure \ref{fig:best_fit_flux}.
+The best fitting model is displayed at 4 phases, as well as the relative error on the flux distribution.
+The error map was generated by drawing 10,000 maps from the MCMC posterior and taking the standard deviation of the fluxes in each segment.
+The offset hot-spot is significant and clearly visible.
+The underlying temperature maps, and the errors in these, are shown in figure \ref{fig:best_fit_temp}.
+
+The correlation between the physical model with the other model parameters can be seen in figure \ref{fig:triangle corner sub}.
+$T_s$ and $\Delta T$ are clearly correlated parameters, since between them they determine the average temperature of the dayside and hence the amplitude of the phase curve.
+$\xi$ is not strongly degenerate with the other parameters.
+This indicates that the $\xi$ parameter is robust to any errors in the absolute flux level of the system.
+
+The fit was repeated with limb darkening enabled to test the impact of the additional radial flexibility on the model.
 The results of both runs are presented In table \ref{tab:results}.
@@
 
-The correlation between the physical model with the other model parameters can be seen in figure \ref{fig:triangle corner sub}.
-$T_s$ and $\Delta T$ are clearly correlated parameters, since between them they determine the average temperature of the dayside and hence the amplitude of the phase curve.
-$\xi$ is not strongly degenerate with the other parameters.
-This indicates that the $\xi$ parameter is robust to any errors in the absolute flux level of the system.
-
-The visual representation of the flux maps for the non-limb darkened case can be seen in figure \ref{fig:best_fit_flux}.
-The best fitting model is displayed at 4 phases, as well as the relative error on the flux distribution.
-The error map was generated by drawing 10,000 maps from the MCMC posterior and taking the standard deviation of the fluxes in each segment.
-The offset hot-spot is significant and clearly visible.
-The underlying temperature maps, and the errors in these, are shown in figure \ref{fig:best_fit_temp}.
-
-The model fit implies that the nightside of the planet is significantly hotter than expected at 1290 $\pm 39$ K, whereas it is not significantly detected in \citet{Stevenson2014}.
-If the nightside has been detected, the flux immediately before and after primary transit should be significantly different to the star-only flux visible during the secondary eclipse.
-Drawing 10,000 lightcurves from the parameters in the non-limb darkened MCMC posterior, we plot the median, 1 sigma and 3 sigma contours for the lightcurve in figure \ref{fig:model}.
-The flux is found to be greater than 1.0 at the 3 sigma level.
-
 \begin{figure}
@@
 
-The fit with limb darkening finds a significantly fainter night side flux, suggesting that the nightside flux is an artifact of using a simple physical model.
+That the fit with limb darkening enabled finds a significantly fainter night side flux suggests that the nightside flux may be an artifact of using a simple physical model.
 This may be due to a correlation between model parameters making the fit inflexible and the simultaneous fit with the systematics model.
 Alternatively, the model may be unable to parametrise a feature of the nightside that is blocking the emitted flux, such as clouds.
-
-However, we emphasize that the $\xi$ parameter does not seem to be effected, which raises our confidence in the robustness of the fit to any potential errors in the symmetric radial component of the surface map.
 
@@
 
-The flat model gave a value of -0.36 - note that this is a good match to the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF
+We test for the dependence of the value of \xi
+
+The flat model gave a value of -0.36 - which is consistent with the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF
 

### 2017-08-14 ms.tex
Update on Overleaf.

@@
 
-As well as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter \citep{Rauscher2007}.
+As well as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter \citep{Rauscher2006}.
 This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress.
@@
 For example, if there are two collision points between the outer arc and the edge of the star, then this falls into the case where the occulted area can be described by the sum of two circular segments.
-Other cases include larger numbers of components, but can still be described by a small number of circle segments and triangles.
+Other cases include larger numbers of components, but can still be described by a small number of circle segments and triangles, a list of the major classes are given below.
+
+An individual segment is defined as having an inner and outer circle edge, and a first and second "outer" edge, which is the radial line from the center of the planet.
+
+\subsubsection{Case 1: zero collisions}
+The trivial case where the segment is either entirely blocked, or entirely unobscured.
+If the distance from the center of the segment to the center of the star is less than the stellar radius then the entire area is added, otherwise nothing is.
+
+\subsubsection{Case 2: Inner and outer circles crossed once}
+The case where both the inner and outer circle segments are both intersected by the disc of the star, and the straight edges are untouched. In this case the total area is calculated as follows
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 - A_4
+\end{equation}
+$A_1$ is the circle segment of the stellar disc bounded by the intersection points with the inner and outer circles.
+$A_2$ is the circle segment of the outer circle edge bounded by the intersection point with the stellar disc and the first straight edge.
+$A_3$ is the quadrilateral with the edges defined by the two intersection points and the end points of the straight edge that is within the stellar disc.
+$A_4$ is the circle segment of the circle segment of the inner circle edge bounded by the intersection point with the stellar disc and the straight edge.
+
+\subsubsection{Case 3: Inner and outer circles crossed once, one straight edge crossed twice.}
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
+\end{equation}
+
+This is calculated the same as Case 2, but an additional area element is subtracted, $A_5$, which is the circle segment formed by the disc of the star and the two intersection points with the straight edge.
+
+\subsubsection{Case 4: inner edge crossed twice, both straight edges crossed.}
+
+this one has two subcases
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 - A_3 - A_4 - A_5 - A_6
+\end{equation}
+
+$A_1$ is the area of the triangle formed by the contact point and two corners interior to the stellar disc. $A_2$ is
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
+\end{equation}
 
@@
 		\includegraphics[width=\columnwidth]{img/all_models.pdf}
-		\caption{This alright fit to Xi as a function of wavelength. blue: flat line, green: gradient function, orange: step function}
+		\caption{The values of log($\xi$) as a function of wavelength.
+Several simple models are fit to the data to test for wavelength dependence.
+A flat line in blue, a gradient model in green and a step function in orange.}
 		\label{fig:best_fit_flux}
@@
 
-We test for the dependence of the value of \xi
-
-The flat model gave a value of -0.36 - which is consistent with the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF
+We test if there is a significant dependence of the value of $\log(\xi)$ on the wavelength by attempting to fit several simple models to the data.
+The null model, which assumes there is no dependence on wavelength is simply a flat line.
+This model gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF with a best fitting value of -0.36 - which is consistent with the white light value.
 
@@
 
-The best fitting model was the step function model with a dividing wavelength of 1.4225 microns, and step values of -0.5242412 -0.2149221. This gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.
+A function approximating a step function might be expected, since the wavelength region covers the water band;values inside the water band will probe lower pressures than those outside, due to the increased optical depth.
+To test for such a feature, we use a step function with three parameters: $\delta_{out}$, which is the average value outside of the step function, $\delta_{in}$ which is the value on the other side of the step, and $\gamma$, which is the wavelength which separates the two sides of the step function.
+The best fitting model was found to have $\gamma$ of 1.4225 microns, which is close to what would be expected for a water features, $\delta_{out}$ of -0.5242412 and $\delta_{in}$ of -0.2149221.
+This model gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.
 
+Using a Bayesian Information Criterion, the improvement of chi2 is marginal for the gradient model and the step function model, and not enough to constitute significant evidence in favour of either model, so we prefer the interpretation of a flat line.
 While we find that there is weak evidence for a trend with wavelength in the data, the flat line model provides a satisfactory fit to the data.
+A full treatment would require calculating the pressure contribution function for each wavelength as was done in \citet{Stevenson2014}, which is beyond the scope of this work.
 

### 2017-08-18 ms.tex
Update on Overleaf.

@@
 
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=\columnwidth]{img/diagram.pdf}
+		\caption{An example of the area calculation algorithm.
+Here the planet (light orange) passes behind the star (light blue).
+The occulted area of the highlighted region defined by the corners C$_1$,  C$_2$, C$_3$ and C$_4$ is calculated.
+The disc of the star intersects with the boundary of the region at I$_1$ and I$_2$.
+The overlapping area can be recovered exactly as the sum of two circle segments (blue and orange) and a triange (green}
+		\label{fig:collision}
+	\end{center}
+\end{figure}
+
 For example, if there are two collision points between the outer arc and the edge of the star, then this falls into the case where the occulted area can be described by the sum of two circular segments.
@@
 
-An individual segment is defined as having an inner and outer circle edge, and a first and second "outer" edge, which is the radial line from the center of the planet.
+An individual region is defined as having an inner and outer circle edge, and a first and second straight edge, which is the radial line from the center of the planet.
+Definitions are given in terms of the intersection points with the stellar disc, and the corners of the region.
+The two corners closest to the center of the planet are reffered to as "inner" and the other two as "outer" corners.
 
-\subsubsection{Case 1: zero collisions}
-The trivial case where the segment is either entirely blocked, or entirely unobscured.
-If the distance from the center of the segment to the center of the star is less than the stellar radius then the entire area is added, otherwise nothing is.
+An example of one geometric case is given below, the remaining 11 cases are listed in the Apendix.
 
-\subsubsection{Case 2: Inner and outer circles crossed once}
-The case where both the inner and outer circle segments are both intersected by the disc of the star, and the straight edges are untouched. In this case the total area is calculated as follows
-\begin{equation} \label{eq:inner_outer}
-A_{tot} = A_1 + A_2 + A_3 - A_4
-\end{equation}
-$A_1$ is the circle segment of the stellar disc bounded by the intersection points with the inner and outer circles.
-$A_2$ is the circle segment of the outer circle edge bounded by the intersection point with the stellar disc and the first straight edge.
-$A_3$ is the quadrilateral with the edges defined by the two intersection points and the end points of the straight edge that is within the stellar disc.
-$A_4$ is the circle segment of the circle segment of the inner circle edge bounded by the intersection point with the stellar disc and the straight edge.
+\subsection{Case 1: Outer circle crossed once, one straight edge crossed once.}
 
-\subsubsection{Case 3: Inner and outer circles crossed once, one straight edge crossed twice.}
+This case takes two forms, either 1 corner is blocked by the star, or three are.
+
+This case for when one corner is blocked is illustrated in figure \ref{collision}, the total blocked area is recovered from the sum of three elements:
 
 \begin{equation} \label{eq:inner_outer}
-A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
+A_{tot} = A_1 + A_2 + A_3
 \end{equation}
 
-This is calculated the same as Case 2, but an additional area element is subtracted, $A_5$, which is the circle segment formed by the disc of the star and the two intersection points with the straight edge.
+$A_1$ is the circle segment of the outer circular edge of the planet beteen the intersection point and the outer corner blocked by the stellar disc.
+A$_2$ is the the circle segment of the stellar disc between the two intersection points.
+A$_3$ is the triangle formed by the two intersection points and the corner blocked by the disc.
+In figure \ref{collision}, areas A$_1$, A$_2$ and A$_3$ are colloured in orange, blue and green, respectively.
 
-\subsubsection{Case 4: inner edge crossed twice, both straight edges crossed.}
-
-this one has two subcases
+If instead the case is flipped such that 3 corners are blocked:
 
 \begin{equation} \label{eq:inner_outer}
-A_{tot} = A_1 + A_2 - A_3 - A_4 - A_5 - A_6
+A_{tot} = A_R - (A_1 + A_2 - A_3)
 \end{equation}
 
-$A_1$ is the area of the triangle formed by the contact point and two corners interior to the stellar disc. $A_2$ is
-
-\begin{equation} \label{eq:inner_outer}
-A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
-\end{equation}
+$A_R$ is the total area of the region.
+$A_1$ is the segment of the outer circle edge defined by the corner that is outside of the stellar disc and the intersection point.
+$A_2$ is the triangle defined by the two intersection points and the corner that is not blocked by the disc.
+$A_3$ is the circle segment defined by the stellar disc and the two intersection points.
 
@@
 
-%\appendix
+\appendix
 
-%\section{Some extra material}
+\section{All colision cases}
+
+\subsection*{Case 2: zero collisions}
+The trivial case where the segment is either entirely blocked, or entirely unobscured.
+If the distance from the center of the segment to the center of the star is less than the stellar radius then the entire area is added, otherwise nothing is.
+
+\subsection*{Case 3: Inner and outer circles crossed once}
+The case where both the inner and outer circle segments are both intersected by the disc of the star, and the straight edges are untouched. In this case the total area is calculated as follows
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 - A_4
+\end{equation}
+$A_1$ is the circle segment of the stellar disc bounded by the intersection points with the inner and outer circles.
+$A_2$ is the circle segment of the outer circle edge bounded by the intersection point with the stellar disc and the outer corner that is blocked by the stellar disc.
+$A_3$ is the quadrilateral defined by the two intersection points and the two corners blocked by the stellar disc.
+$A_4$ is the circle segment of the inner circle edge bounded by the intersection point with the stellar disc and the inner corner that is blocked by the star.
+
+\subsection*{Case 4: Inner and outer circles crossed once, one straight edge crossed twice.}
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
+\end{equation}
+
+This is calculated the same as Case 2, but an additional area element is subtracted, $A_5$, which is the circle segment formed by the disc of the star and the two intersection points with the straight edge.
+
+\subsection*{Case 5: inner edge crossed twice, both straight edges crossed.}
+
+this one has two subcases; if the inner edges are covered by the star, then:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_R - (A_1 + A_2 + A_3 - A_4 - A_5)
+\end{equation}
+
+$A_R$ is the total area of the region.
+
+otherwise, if the inner edges are outside the disc of the star:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_R - (A_1 + A_2 - A_3 - A_4 - A_5 - A_6)
+\end{equation}
+
+$A_R$ is the total area of the region.
+$A_1$ is the area of the triangle formed by the two corners on one straight edge, and the contact point with the inner edge that is closest to them, $A_2$ is the same for the other side.
+A$_3$ and A$_4$ are the circle segments of the inner edge, each formed by an inner corner and the intersection of the inner edge that is closest to them.
+A$_5$ and A$_6$ are the circle segments of the stellar disc, each formed by an intersection of a straight edge and the intersection of the inner edge that is closest to them.
+
+\subsection*{Case 6: A straight edge crossed twice}
+
+In this case, only a single area needs to be calculated, the area of a circle segment defined by the stellar disc, and the two intersection points
+
+\subsection*{Case 7: Inner edge and one straight edge}
+
+Similar to Case 2, this case has two subcases, one where there are three blocked corners, and one where one corner is blocked. For the case with one corner inside:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 - A_3
+\end{equation}
+
+$A_1$ is the triangle defined by the corner that is blocked by the disc and the two intersection points.
+$A_2$ is the circle segment of the star disc defined by the two intersection points.
+$A_3$ is the segment area of the inner edge defined by the intersection point and the corner that is blocked by the stellar disc.
+
+For the case with three corners inside:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_R - (A_1 - A_2 - A_3)
+\end{equation}
+
+$A_R$ is the total area of the region.
+$A_1$ is the segment of the inner edge defined by the intersection point and the corner not blocked by the star.
+$A_2$ is the segment of the star defined by the intersection and the corner not blocked by the star.
+$A_3$ is the triangle defined by the corner not blocked by the star and the two intersection points.
+
+\subsection*{Case 8: Outer edge crossed twice}
+
+If no corners are covered by the star, then this is simply the sum of two circle segments, for the outer edge and the star, defined by the two interestion points.
+
+If all corners are covered by the star, then:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_R - (A_1 - A_2)
+\end{equation}
+
+Where $A_1$ is the segment of the outer edge defined by the two interestion points, and $A_2$ is the segment of the stellar disc defined by the two interestion points.
+
+\subsection*{Case 9: Both edges crossed}
+
+This is divided further into two subcases, if the two outer corners are covered by the star, then:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3
+\end{equation}
+
+$A_1$ is the quadrilateral defined by the intersection points and the outer corners.
+$A_2$ is the circle segment defined by the stellar disc and the intersection points.
+$A_3$ is the circle segment defined by the outer edge and the outer corners.
+
+Otherwise, if the two inner corners are covered:
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 - A_3
+\end{equation}
+
+$A_1$ is the quadrilateral defined by the intersection points and the inner edges.
+$A_2$ is the circle segment defined by the stellar disc and the intersection points.
+$A_3$ is the circle segment defined by the inner edge and the inner corners.
+
+\subsection*{Case 10: 2 inner, one outer, one edge}
+
+\subsection*{Case 11: 2 inner, two outer}
+
+This case only occurs when the star is smaller than the planet.
+
+\begin{equation} \label{eq:inner_outer}
+A_{tot} = A_1 + A_2 + A_3 + A_4 - A_5
+\end{equation}
+
+$A_1$ is the quadrilateral formed by the 4 intersection points.
+$A_2$ and $A_3$ are the circle segments of the stellar disc defined by the two pairs of inner and outer intersection points.
+$A_4$ is the circle segment of the outer edge formed by the two intersection points on the outer edge.
+$A_5$ is the circle segment of the outer edge formed by the two intersection points on the inner edge.
+
+\subsection*{Case 12: tangent solutions}
+
+The remaining posible cases are all tangent solutions, where the disc of the star touches the boundary of the region exactly once, and no area is blocked.
 
